### Tissue and cell type enrichment

<br>

::: { .callout-note}

## Synopsis

* Using consensus transcript expression data from the [Human Protein Atlas (HPA)](https://www.proteinatlas.org/humanproteome/tissue), we assess whether genes in the query set are preferentially expressed in specific tissues or cell types
  * Tissue data covers [51 normal tissue types](https://www.proteinatlas.org/humanproteome/tissue/data#consensus_tissues_rna) (consensus of HPA and GTEx). Expression unit: [_normalized_ transcripts pr million (nTPM)](https://www.proteinatlas.org/humanproteome/tissue/method/transcriptomics)
  * Cell type data covers [53 cell type groups](https://www.proteinatlas.org/humanproteome/single+cell/single+cell+type/data#cell_type_group_data) derived from single-cell RNA-seq. Expression unit: [nCPM](https://www.proteinatlas.org/humanproteome/tissue/method/transcriptomics)
* Two complementary analyses are provided for each resolution (tissue/cell type):
  1. **Expression specificity**: for each query gene, a _tau_ index (0 = ubiquitously expressed, 1 = highly tissue/cell-type-specific; [Yanai et al., Bioinformatics, 2005](https://doi.org/10.1093/bioinformatics/bti042)), along with its most highly expressed context(s)
  2. **Enrichment**: for each tissue/cell type, a hypergeometric test of whether query genes are overrepresented among the genes most highly expressed there (top 25% by expression) - only contexts with an adjusted (Benjamini-Hochberg) p-value < `r onc_enrich_report[['config']][['cell_tissue']][['fdr_threshold']]` are listed

:::

<br>

#### Target set - tissue specificity

<br>

```{r tissue_tau_dist}
#| echo: false
#| eval: !expr NROW(onc_enrich_report[['data']][['cell_tissue']][['tissue_overview']][['tau_distribution']]) > 0

tissue_tau_fig <- plotly::plot_ly(
  data = onc_enrich_report[['data']][['cell_tissue']][['tissue_overview']][['tau_distribution']],
  x = ~tau,
  color = ~gene_set,
  colors = c("Query set" = "#B2182B",
             "All protein-coding genes" = "#4393C3"),
  type = "histogram",
  histnorm = "probability density",
  opacity = 0.65,
  hovertemplate = paste(
    "Tau: %{x}",
    "Density: %{y}",
    "<extra></extra>",
    sep = "<br>")) |>
  plotly::layout(
    barmode = "overlay",
    height = 400,
    width = 800,
    xaxis = list(
      title = list(text = "Tissue specificity (tau index)",
                  font = list(size = 15, family = "Helvetica")),
      tickfont = list(size = 14, family = "Helvetica")),
    yaxis = list(
      title = list(text = "Density",
                  font = list(size = 15, family = "Helvetica")),
      tickfont = list(size = 14, family = "Helvetica")),
    legend = list(orientation = "h", x = 0.1, y = -0.25,
                 font = list(size = 13, family = "Helvetica"))
  )

tissue_tau_fig
rm(tissue_tau_fig)

```
<br><br>

::: {.panel-tabset}

##### Specificity per target gene

```{r tissue_tau_per_gene}
#| echo: false
#| output: asis

DT::datatable(
  onc_enrich_report[['data']][['cell_tissue']][['tissue_overview']][['per_gene']] |>
    dplyr::select(-cancer_max_rank),
  escape = F,
  extensions=c("Buttons","Responsive"),
  width = "100%",
  style = 'bootstrap5',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  ) |>
  DT::formatRound(columns = "tau", digits = 3)

```
<br><br>

##### Enrichment - query set

<br>

```{r filter_tissue_enrichment}
#| echo: false
#| output: asis

tissue_enrichment_sig <-
  onc_enrich_report[['data']][['cell_tissue']][['tissue_enrichment']][['per_type']] |>
  dplyr::filter(
    p_adjusted < onc_enrich_report[['config']][['cell_tissue']][['fdr_threshold']])

num_significant_tissues <- nrow(tissue_enrichment_sig)

tissue_enrichment_plot_df <- tissue_enrichment_sig |>
  dplyr::arrange(p_adjusted) |>
  head(30) |>
  dplyr::mutate(
    neg_log10_fdr = -log10(p_adjusted),
    ## trailing spaces push the (right-anchored) tick label away from
    ## the axis line, giving visible breathing room
    tissue_label = paste0(tissue, "   "),
    hover_text = paste0(
      "N query genes: ", n_query_genes, "<br>",
      "N background genes: ", n_background_genes))

## Height of the enrichment bar plot scales with the number of contexts
## shown - both the plotly widget itself (pixels) and the surrounding
## quarto output cell (fig-height, inches) need to agree, otherwise the
## widget renders taller than its container and scrolls internally
tissue_enrichment_fig_height_px <-
  400 + (14.67 * max(NROW(tissue_enrichment_plot_df), 1))
tissue_enrichment_fig_height_in <- tissue_enrichment_fig_height_px / 96

```

```{r no_significant_tissues}
#| echo: false
#| output: asis
#| eval: !expr num_significant_tissues == 0

cat('<br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;Considering the tissue expression specificity of members of the query set, <b>NO TISSUES</b> are significantly enriched (adjusted p-value < 0.05) compared to the background. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')

```

```{r significant_tissues_plot}
#| echo: false
#| eval: !expr num_significant_tissues > 0
#| fig-height: !expr tissue_enrichment_fig_height_in

tissue_enrichment_fig <- plotly::plot_ly(
  data = tissue_enrichment_plot_df,
  x = ~fold_enrichment,
  y = ~stats::reorder(tissue_label, fold_enrichment),
  type = "bar",
  orientation = "h",
  text = ~hover_text,
  textposition = "none",
  marker = list(
    color = ~neg_log10_fdr,
    colorscale = "Reds",
    showscale = TRUE,
    colorbar = list(
      title = list(text = "-log10(FDR)",
                  font = list(size = 13, family = "Helvetica")),
      tickfont = list(size = 13, family = "Helvetica"))),
  hovertemplate = paste(
    "Tissue: %{y}",
    "Fold enrichment: %{x}",
    "%{text}",
    "<extra></extra>",
    sep = "<br>")) |>
  plotly::layout(
    height = tissue_enrichment_fig_height_px,
    width = 800,
    xaxis = list(
      title = list(text = "Fold enrichment",
                  font = list(size = 15, family = "Helvetica")),
      tickfont = list(size = 14, family = "Helvetica")),
    yaxis = list(title = "",
                tickfont = list(size = 14, family = "Helvetica"),
                automargin = TRUE),
    margin = list(l = 170)
  )

tissue_enrichment_fig
rm(tissue_enrichment_fig, tissue_enrichment_plot_df)

```
<br><br>

```{r significant_tissues_table}
#| echo: false
#| output: asis
#| eval: !expr num_significant_tissues > 0

DT::datatable(
  tissue_enrichment_sig,
  escape = F,
  extensions=c("Buttons","Responsive"),
  width = "100%",
  style = 'bootstrap5',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  ) |>
  DT::formatSignif(columns = "fold_enrichment", digits = 3) |>
  DT::formatSignif(columns = c("p_adjusted","p_value"), digits = 3)

```
<br><br>

:::

#### Target set - cell type specificity

<br>

```{r celltype_tau_dist}
#| echo: false
#| eval: !expr NROW(onc_enrich_report[['data']][['cell_tissue']][['scRNA_overview']][['tau_distribution']]) > 0

celltype_tau_fig <- plotly::plot_ly(
  data = onc_enrich_report[['data']][['cell_tissue']][['scRNA_overview']][['tau_distribution']],
  x = ~tau,
  color = ~gene_set,
  colors = c("Query set" = "#B2182B",
             "All protein-coding genes" = "#4393C3"),
  type = "histogram",
  histnorm = "probability density",
  opacity = 0.65,
  hovertemplate = paste(
    "Tau: %{x}",
    "Density: %{y}",
    "<extra></extra>",
    sep = "<br>")) |>
  plotly::layout(
    barmode = "overlay",
    height = 400,
    width = 800,
    xaxis = list(
      title = list(text = "Cell type specificity (tau index)",
                  font = list(size = 15, family = "Helvetica")),
      tickfont = list(size = 14, family = "Helvetica")),
    yaxis = list(
      title = list(text = "Density",
                  font = list(size = 15, family = "Helvetica")),
      tickfont = list(size = 14, family = "Helvetica")),
    legend = list(orientation = "h", x = 0.1, y = -0.25,
                 font = list(size = 13, family = "Helvetica"))
  )

celltype_tau_fig
rm(celltype_tau_fig)

```
<br><br>

::: {.panel-tabset}

##### Specificity per target gene

```{r celltype_tau_per_gene}
#| echo: false
#| output: asis

DT::datatable(
  onc_enrich_report[['data']][['cell_tissue']][['scRNA_overview']][['per_gene']] |>
    dplyr::select(-cancer_max_rank),
  escape = F,
  extensions=c("Buttons","Responsive"),
  width = "100%",
  style = 'bootstrap5',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  ) |>
  DT::formatRound(columns = "tau", digits = 3)

```
<br><br>

##### Enrichment - query set

<br>

```{r filter_celltype_enrichment}
#| echo: false
#| output: asis

celltype_enrichment_sig <-
  onc_enrich_report[['data']][['cell_tissue']][['scRNA_enrichment']][['per_type']] |>
  dplyr::filter(
    p_adjusted < onc_enrich_report[['config']][['cell_tissue']][['fdr_threshold']])

num_significant_celltypes <- nrow(celltype_enrichment_sig)

celltype_enrichment_plot_df <- celltype_enrichment_sig |>
  dplyr::arrange(p_adjusted) |>
  head(30) |>
  dplyr::mutate(
    neg_log10_fdr = -log10(p_adjusted),
    ## trailing spaces push the (right-anchored) tick label away from
    ## the axis line, giving visible breathing room
    cell_type_label = paste0(cell_type, "   "),
    hover_text = paste0(
      "N query genes: ", n_query_genes, "<br>",
      "N background genes: ", n_background_genes))

## Height of the enrichment bar plot scales with the number of contexts
## shown - both the plotly widget itself (pixels) and the surrounding
## quarto output cell (fig-height, inches) need to agree, otherwise the
## widget renders taller than its container and scrolls internally
celltype_enrichment_fig_height_px <-
  400 + (14.67 * max(NROW(celltype_enrichment_plot_df), 1))
celltype_enrichment_fig_height_in <- celltype_enrichment_fig_height_px / 96

```

```{r no_significant_celltypes}
#| echo: false
#| output: asis
#| eval: !expr num_significant_celltypes == 0

cat('<br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;Considering the cell-type expression specificity of members of the query set, <b>NO CELL TYPES</b> are significantly enriched (adjusted p-value < 0.05) compared to the background. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')

```

```{r significant_celltypes_plot}
#| echo: false
#| eval: !expr num_significant_celltypes > 0
#| fig-height: !expr celltype_enrichment_fig_height_in

celltype_enrichment_fig <- plotly::plot_ly(
  data = celltype_enrichment_plot_df,
  x = ~fold_enrichment,
  y = ~stats::reorder(cell_type_label, fold_enrichment),
  type = "bar",
  orientation = "h",
  text = ~hover_text,
  textposition = "none",
  marker = list(
    color = ~neg_log10_fdr,
    colorscale = "Reds",
    showscale = TRUE,
    colorbar = list(
      title = list(text = "-log10(FDR)",
                  font = list(size = 13, family = "Helvetica")),
      tickfont = list(size = 13, family = "Helvetica"))),
  hovertemplate = paste(
    "Cell type: %{y}",
    "Fold enrichment: %{x}",
    "%{text}",
    "<extra></extra>",
    sep = "<br>")) |>
  plotly::layout(
    height = celltype_enrichment_fig_height_px,
    width = 800,
    xaxis = list(
      title = list(text = "Fold enrichment",
                  font = list(size = 15, family = "Helvetica")),
      tickfont = list(size = 14, family = "Helvetica")),
    yaxis = list(title = "",
                tickfont = list(size = 14, family = "Helvetica"),
                automargin = TRUE),
    margin = list(l = 170)
  )

celltype_enrichment_fig
rm(celltype_enrichment_fig, celltype_enrichment_plot_df)

```
<br><br>

```{r significant_celltypes_table}
#| echo: false
#| output: asis
#| eval: !expr num_significant_celltypes > 0

DT::datatable(
  celltype_enrichment_sig,
  escape = F,
  extensions=c("Buttons","Responsive"),
  width = "100%",
  style = 'bootstrap5',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  ) |>
  DT::formatSignif(columns = "fold_enrichment", digits = 3) |>
  DT::formatSignif(columns = c("p_adjusted","p_value"), digits = 3)

```
<br><br>

:::
