### Drug associations

::: {.callout-note}
## Synopsis

* Each protein/protein in the query set is annotated with:
   * Targeted drugs (inhibitors/antagonists), as found through the [Open Targets Platform](https://targetvalidation.org), limited to compounds indicated for a cancer condition/phenotype
   * Drugs are organized into the following buckets:
       * Targeted cancer drugs in early clinical development (phase 1/2)(column <b>drugs_early_phase</b>)
       * Targeted cancer drugs in late clinical development (phase 3/4) (column <b>drugs_late_phase</b>)
       * <i>Approved drugs</i> - here also showing the (cancer type) indications for which the drugs are approved for

:::

<br>

```{r table_browse_drug_targets}
#| echo: false
#| output: asis
#| eval: !expr NROW(onc_enrich_report[['data']][['drug']][['target_drugs']]) > 0

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['drug']][['target_drugs']], escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))



```


```{r drug_targets_missing}
#| echo: false
#| output: asis
#| eval: !expr NROW(onc_enrich_report[['data']][['drug']][['target_drugs']]) == 0

cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> query proteins with cancer drug associations from Open Targets Platform were found. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br>

#### Target tractabilities

::: {.panel-tabset}

* Each gene/protein in the query set is annotated with _[target tractability information](https://docs.targetvalidation.org/getting-started/target-tractability)_ (also known as _druggability_) towards
small molecules/compounds and antibodies
* Query genes are colored in varying shades of purple (from <span style="background-color:#b8b8ba; padding:2x; color:white">&nbsp;unknown tractability&nbsp;</span> to <span style="background-color:#810f7c; padding:2x; color:white">&nbsp;clinical precedence&nbsp;</span>)
   

<br><br>

##### Small molecules/compounds 

```{r table_browse_tractability_sm}
#| echo: false
#| output: asis
#| eval: true

htmltools::br()

tractable_targets_sm <- onc_enrich_report[['data']][['drug']][['tractability_sm']] |>
  dplyr::filter(!is.na(SM_tractability_category) & 
                  SM_tractability_category != "Unknown")

DT::datatable(tractable_targets_sm, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), dom = 'Bfrtip')) |>
   DT::formatStyle(
    "SM_tractability_category", 
    color = "white",
    backgroundColor = DT::styleEqual(
      onc_enrich_report[["config"]][["drug"]][["sm_levels"]],
      onc_enrich_report[["config"]][["drug"]][["sm_levels_colors"]]
    )
  )



```

<br><br>

##### Antibodies

```{r table_browse_tractability_ab}
#| echo: false
#| output: asis
#| eval: true

htmltools::br()

tractable_targets_ab <- onc_enrich_report[['data']][['drug']][['tractability_ab']] |>
  dplyr::filter(!is.na(AB_tractability_category) & 
                  AB_tractability_category != "Unknown")

DT::datatable(tractable_targets_ab, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), dom = 'Bfrtip')) |>
   DT::formatStyle(
    "AB_tractability_category", 
    color = "white",
    backgroundColor = DT::styleEqual(
      onc_enrich_report[["config"]][["drug"]][["ab_levels"]],
      onc_enrich_report[["config"]][["drug"]][["ab_levels_colors"]]
    )
  )



```


<br><br>

:::
