### Function and pathway enrichment

::: {.callout-note}
## Synopsis

-   The query set is analyzed with [clusterProfiler](https://bioconductor.org/packages/release/bioc/vignettes/clusterProfiler/inst/doc/clusterProfiler.html) for functional enrichment/over-representation with respect to:
    -   [Gene Ontology terms](https://geneontology.org). All three subontologies: *Molecular Function* (GO_MF), *Cellular Component* (GO_CC) & *Biological Process* (GO_BP)
    -   Molecular signalling networks from [KEGG](https://www.genome.jp/kegg/pathway.html)
    -   Cellular pathways from [Reactome](https://reactome.org/), and other curated gene signature sets from the [Molecular Signatures Database (MSiGDB)](http://software.broadinstitute.org/gsea/msigdb/index.jsp)
    -   [WikiPathways](https://www.wikipathways.org/index.php/Special:BrowsePathways)
    -   Manually curated signal transduction pathways from [NetPath](http://www.netpath.org)

-   Enrichment/over-representation test settings (*clusterProfiler*)
    -   P-value cutoff: **`r onc_enrich_report[['config']][['enrichment']][['p_value_cutoff']]`**
    -   Q-value cutoff: **`r onc_enrich_report[['config']][['enrichment']][['q_value_cutoff']]`**
    -   Correction for multiple testing: **`r onc_enrich_report[['config']][['enrichment']][['p_adjust_method']]`**
    -   Minimal size of genes annotated by term for testing: **`r onc_enrich_report[['config']][['enrichment']][['min_gs_size']]`**
    -   Maximal size of genes annotated by term for testing: **`r onc_enrich_report[['config']][['enrichment']][['max_gs_size']]`**
    -   Background gene set description: **`r onc_enrich_report[['config']][['enrichment']][['bgset_description']]`**
    -   Background gene set size: **`r onc_enrich_report[['config']][['enrichment']][['bgset_size']]`**
    -   Remove redundancy of enriched GO terms: **`r onc_enrich_report[['config']][['enrichment']][['simplify_go']]`**

:::

<br>

```{r prepare_enrichment_data}
#| echo: false
#| output: asis

show_enrichment_filters <- list()
eitems <- list()
active_tab <- list()
for(type in c('go','msigdb','kegg','wikipathways','netpath')) {
  show_enrichment_filters[[type]] <- F
  active_tab[[type]] <- F
  if (NROW(onc_enrich_report[['data']][['enrichment']][[type]]) > 0) {
    show_enrichment_filters[[type]] <- T
  }
}

plot_fontsize <- 10

subontology_plots <- list()
subontology_plots[['ALL']] <- T
subontology_plots[['BP']] <- T
subontology_plots[['MF']] <- T
subontology_plots[['CC']] <- T

#for(ont in c('GO_BP','GO_CC','GO_MF')) {
if (show_enrichment_filters[['go']] == T) {
  subont_bp <- onc_enrich_report[['data']][['enrichment']][['go']] |>
    dplyr::filter(db == 'GO_BP')
  
  if (nrow(subont_bp) <= 2) {subontology_plots[['BP']] <- F}
  
  subont_mf <- onc_enrich_report[['data']][['enrichment']][['go']] |>
    dplyr::filter(db == 'GO_MF')
  
  if (nrow(subont_mf) <= 2) {subontology_plots[['MF']] <- F}
  
  subont_cc <- onc_enrich_report[['data']][['enrichment']][['go']] |>
    dplyr::filter(db == 'GO_CC')
  
  if (nrow(subont_cc) <= 2) {subontology_plots[['CC']] <- F}
  
}else{
  subontology_plots[['ALL']] <- F
  subontology_plots[['MF']] <- F
  subontology_plots[['BP']] <- F
  subontology_plots[['CC']] <- F
}


## Set active tabs
if (show_enrichment_filters[['go']] == T) {
  active_tab[['go']] <- T
}else{
  if (show_enrichment_filters[['msigdb']] == T) {
      active_tab[['msigdb']] <- T
  }
  else{
    if (show_enrichment_filters[['kegg']] == T) {
      active_tab[['kegg']] <- T
    }
    else{
      if (show_enrichment_filters[['wikipathways']] == T) {
        active_tab[['wikipathways']] <- T
      }
      else{
        if (show_enrichment_filters[['netpath']] == T) {
          active_tab[['netpath']] <- T
        }
      }
    }
  }
}

## If no content in enrichment tables, set GO to active tab
if (active_tab[['go']] == F & active_tab[['msigdb']] == F &
   active_tab[['kegg']] == F & active_tab[['wikipathways']] == F &
   active_tab[['netpath']] == F) {
  active_tab[['go']] <- T
}




```

#### Enrichment tables

<br>

::: panel-tabset
<br>

```{r active_tab_go}
#| echo: false
#| output: asis

if (active_tab[['go']] == T) {
  cat("")
  cat("##### Gene Ontology {.active}")
  cat("")
}else{
  cat("")
  cat("##### Gene Ontology")
  cat("")
}
```

<br>

```{r table_browse_go}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['go']]


enrichment_go_display <- onc_enrich_report[['data']][['enrichment']][['go']] |>
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue, 
                P_Value = pvalue, 
                Gene_Members = gene_symbol_link, 
                DB = db,
                Exact_Source = exact_source, 
                Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio) |> 
   dplyr::select(Term, Enrichment, Q_Value, Gene_Members, DB,  
                Background_Ratio, Gene_Ratio) |> 
  dplyr::arrange(Q_Value)


terms_go <- crosstalk::SharedData$new(enrichment_go_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_go, ~Enrichment)
  ),
  list(
    crosstalk::filter_select("DB", "Ontology", terms_go, ~DB)

  )
)

htmltools::br()
DT::datatable(
  terms_go, 
  escape = F, 
  extensions = c("Buttons","Responsive"), 
  width = "100%",
  options = list(buttons = c('csv','excel'), 
                 dom = 'Bfrtip')
)
rm(terms_go)
rm(enrichment_go_display)


```

<br>

```{r go_missing}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['go']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No gene ontology terms were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>', sep = '\n')
cat('\n')
cat('<br><br>')

```

<br>

```{r active_tab_msigdb}
#| echo: false
#| output: asis

if (active_tab[['msigdb']] == T) {
  cat("")
  cat("##### Molecular Signatures Database (MSigDB) {.active}")
  cat("")
}else{
  cat("")
  cat("##### Molecular Signatures Database (MSigDB)")
  cat("")
}
```

<br>

```{r table_browse_msigdb}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['msigdb']]

enrichment_msigdb_display <- onc_enrich_report[['data']][['enrichment']][['msigdb']] |>
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue,  
                P_Value = pvalue,
                Gene_Members = gene_symbol_link, 
                DB = db,
                Exact_Source = exact_source, 
                Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio) |>
  dplyr::select(Term, Enrichment, Q_Value, Gene_Members, DB,  
                Background_Ratio, Gene_Ratio) |>
  dplyr::arrange(Q_Value)

terms_msigdb <- crosstalk::SharedData$new(enrichment_msigdb_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_msigdb, ~Enrichment)
  ),
  list(
    crosstalk::filter_select("DB", "Signature collection", terms_msigdb, ~DB)

  )
)

htmltools::br()
DT::datatable(terms_msigdb, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), 
                           dom = 'Bfrtip')
)
rm(terms_msigdb)
rm(enrichment_msigdb_display)
```

<br>

```{r msigdb_missing}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['msigdb']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No signatures from the Molecular Signature Database (MSIGdb) were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br>

```{r active_tab_kegg}
#| echo: false
#| output: asis

if (active_tab[['kegg']] == T) {
  cat("")
  cat("##### KEGG pathways {.active}")
  cat("")
}else{
  cat("")
  cat("##### KEGG pathways")
  cat("")
}
```

<br>

```{r table_browse_kegg}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['kegg']]
enrichment_keggdb_display <- onc_enrich_report[['data']][['enrichment']][['kegg']] |>
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue,  
                P_Value = pvalue,
                Gene_Members = gene_symbol_link, 
                DB = db,
                Exact_Source = exact_source, 
                Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio) |>
  dplyr::select(Term, Enrichment, Q_Value, Gene_Members, DB,  
                Background_Ratio, Gene_Ratio) |>
  dplyr::arrange(Q_Value)

terms_keggdb <- crosstalk::SharedData$new(enrichment_keggdb_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_keggdb, ~Enrichment)
  )
)

htmltools::br()
DT::datatable(terms_keggdb, escape = F, extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
)
rm(terms_keggdb)
rm(enrichment_keggdb_display)


```

<br>

```{r keggdb_missing}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['kegg']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No pathways from KEGG  were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>', sep = '\n')
cat('\n')
cat('<br><br>')

```

<br>

```{r active_tab_wikipathways}
#| echo: false
#| output: asis

if (active_tab[['wikipathways']] == T) {
  cat("")
  cat("##### WikiPathways {.active}")
  cat("")
}else{
  cat("")
  cat("##### WikiPathways")
  cat("")
}
```

<br>

```{r table_browse_wikipathwaydb}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['wikipathways']]

enrichment_wikidb_display <- onc_enrich_report[['data']][['enrichment']][['wikipathways']] |>
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue, P_Value = pvalue,
                Gene_Members = gene_symbol_link, DB = db,
                Exact_Source = exact_source, 
                Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio) |> 
   dplyr::select(Term, Enrichment, Q_Value, Gene_Members, 
                 DB, 
                Background_Ratio, Gene_Ratio) |>
  dplyr::arrange(Q_Value)


terms_wikipathway <- crosstalk::SharedData$new(enrichment_wikidb_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_wikipathway, ~Enrichment)
  )
)

htmltools::br()
DT::datatable(
  terms_wikipathway, escape = F, 
  extensions = c("Buttons","Responsive"), 
  width = "100%",
  options = list(buttons = c('csv','excel'), dom = 'Bfrtip')
)

rm(terms_wikipathway)
rm(enrichment_wikidb_display)



```

<br>

```{r wiki_missing}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['wikipathways']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No pathway signatures from WikiPathways were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>', sep = '\n')
cat('\n')
cat('<br><br>')


```

<br>

```{r active_tab_netpath}
#| echo: false
#| output: asis

if (active_tab[['netpath']] == T) {
  cat("")
  cat("##### NetPath {.active}")
  cat("")
}else{
  cat("")
  cat("##### NetPath")
  cat("")
}
```

<br>

```{r table_browse_netpathdb}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['netpath']]

enrichment_netpath_display <- onc_enrich_report[['data']][['enrichment']][['netpath']] |>
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue, P_Value = pvalue,
                Gene_Members = gene_symbol_link, 
                DB = db,
                Exact_Source = exact_source, 
                Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio) |>
   dplyr::select(Term, Enrichment, Q_Value, Gene_Members, 
                 DB, 
                Background_Ratio, Gene_Ratio) |> 
  dplyr::arrange(Q_Value)

terms_netpath <- crosstalk::SharedData$new(enrichment_netpath_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_netpath, ~Enrichment)
  )
)

htmltools::br()
DT::datatable(
  terms_netpath, 
  escape = F, 
  extensions = c("Buttons","Responsive"), 
  width = "100%",
  options = list(buttons = c('csv','excel'), 
                 dom = 'Bfrtip')
)

rm(terms_netpath)
rm(enrichment_netpath_display)

```

<br>

```{r netpath_missing}
#| echo: false
#| output: asis
#| eval: !expr show_enrichment_filters[['netpath']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No signalling pathways from NetPath were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>', sep = '\n')
cat('\n')
cat('<br><br>')


```
:::

<br>

#### GO enrichment plots {.tabset}

<br>

::: panel-tabset
##### Molecular function

```{r go_enrichment_barplot_mf}
#| echo: false
#| output: asis
#| eval: !expr subontology_plots[['MF']]

plot_data <- onc_enrich_report[['data']][['enrichment']][['go']] |>
  dplyr::select(description, enrichment_factor, qvalue, db) |>
  dplyr::filter(db == 'GO_MF') |>
  dplyr::arrange(qvalue) |>
  utils::head(onc_enrich_report[['config']][['enrichment']][['enrichment_plot_num_terms']]) |>
  ## reverse order (to show entries with lowest q-values at the top of the plot)
  dplyr::arrange(dplyr::desc(qvalue)) |>
  dplyr::rename(Subontology = db) |>
  dplyr::mutate(
    Subontology = dplyr::case_when(
      Subontology == "GO_BP" ~ "Biological Process",
      Subontology == "GO_CC" ~ "Cellular Component",
      Subontology == "GO_MF" ~ "Molecular Function",
      TRUE ~ as.character(Subontology)
    ))

plot_data$description <- 
  factor(plot_data$description, levels = plot_data$description)

max_y <- max(plyr::round_any(plot_data$enrichment_factor, 10, f = ceiling))

p <- ggplot2::ggplot(
  plot_data, 
  ggplot2::aes( x = description, y = enrichment_factor, fill = qvalue) ) +
  ggplot2::geom_bar( stat = "identity" ) +
  ggplot2::xlab("") +
  ggplot2::ylab("Enrichment") +
  ggplot2::ylim(0, max_y) +
  ggplot2::theme_classic() +
  ggplot2::coord_flip() +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(size = plot_fontsize, vjust = 0.5),
    axis.text.y = ggplot2::element_text(family = "Helvetica", size = plot_fontsize),
    axis.title.x = ggplot2::element_text(family = "Helvetica", size = plot_fontsize),
    axis.title.y = ggplot2::element_text(family = "Helvetica", size = plot_fontsize)
  )

rm(max_y)

height_plot <- 500
if (nrow(plot_data) <= 15) {
  height_plot <- 400
}
if (nrow(plot_data) <= 10) {
  height_plot <- 300
}

enrichment_barplot <- plotly::ggplotly(p, width = 800, height = height_plot) |>
    plotly::layout(legend = list(orientation = "h", x = -0.2, y = -0.25))

enrichment_barplot
rm(height_plot)
rm(plot_data)

```

```{r go_plot_missing_mf}
#| echo: false
#| output: asis
#| eval: !expr subontology_plots[['MF']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;Enrichment plot omitted: No/limited GO terms were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>', sep = '\n')
cat('\n')
cat('<br><br>')

```

<br><br>

##### Biological Process

```{r go_enrichment_barplot_bp}
#| echo: false
#| output: asis
#| eval: !expr subontology_plots[['BP']]

plot_data <- onc_enrich_report[['data']][['enrichment']][['go']] |>
  dplyr::select(description, enrichment_factor, qvalue, db) |>
  dplyr::filter(db == 'GO_BP') |>
  dplyr::arrange(qvalue) |>
  head(onc_enrich_report[['config']][['enrichment']][['enrichment_plot_num_terms']]) |>
  ## reverse order (to show entries with lowest q-values at the top of the plot)
  dplyr::arrange(dplyr::desc(qvalue)) |>
  dplyr::rename(Subontology = db) |>
  dplyr::mutate(
    Subontology = dplyr::case_when(
      Subontology == "GO_BP" ~ "Biological Process",
      Subontology == "GO_CC" ~ "Cellular Component",
      Subontology == "GO_MF" ~ "Molecular Function",
      TRUE ~ as.character(Subontology)
    ))

plot_data$description <- 
  factor(plot_data$description, levels = plot_data$description)

max_y <- max(plyr::round_any(plot_data$enrichment_factor, 10, f = ceiling))

p <- ggplot2::ggplot(
  plot_data, 
  ggplot2::aes( x = description, y = enrichment_factor, fill = qvalue) ) +
  ggplot2::geom_bar( stat = "identity" ) +
  ggplot2::xlab("") +
  ggplot2::ylab("Enrichment") +
  ggplot2::theme_classic() +
  ggplot2::coord_flip() +
  ggplot2::theme(
    legend.title = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(size = plot_fontsize, vjust = 0.5),
    axis.text.y = ggplot2::element_text(family = "Helvetica", size = plot_fontsize),
    axis.title.x = ggplot2::element_text(family = "Helvetica", size = plot_fontsize),
    axis.title.y = ggplot2::element_text(family = "Helvetica", size = plot_fontsize)
  )

rm(max_y)

height_plot <- 500
if (nrow(plot_data) <= 15) {
  height_plot <- 400
}
if (nrow(plot_data) <= 10) {
  height_plot <- 300
}

enrichment_barplot <- plotly::ggplotly(p, width = 800, height = height_plot) |>
    plotly::layout(legend = list(orientation = "h", x = -0.2, y = -0.25))

enrichment_barplot
rm(height_plot)
rm(plot_data)

```

```{r go_plot_missing_bp}
#| echo: false
#| output: asis
#| eval: !expr subontology_plots[['BP']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;Enrichment plot omitted: No/limited GO terms were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>', sep = '\n')
cat('\n')
cat('<br><br>')

```

<br><br>

##### Cellular Component

```{r go_enrichment_barplot_cc}
#| echo: false
#| output: asis
#| eval: !expr subontology_plots[['CC']]

plot_data <- onc_enrich_report[['data']][['enrichment']][['go']] |>
  dplyr::select(description, enrichment_factor, qvalue, db) |>
  dplyr::filter(db == 'GO_CC') |>
  dplyr::arrange(qvalue) |>
  head(onc_enrich_report[['config']][['enrichment']][['enrichment_plot_num_terms']]) |>
  ## reverse order (to show entries with lowest q-values at the top of the plot)
  dplyr::arrange(dplyr::desc(qvalue)) |>
  dplyr::rename(Subontology = db) |>
  dplyr::mutate(
    Subontology = dplyr::case_when(
      Subontology == "GO_BP" ~ "Biological Process",
      Subontology == "GO_CC" ~ "Cellular Component",
      Subontology == "GO_MF" ~ "Molecular Function",
      TRUE ~ as.character(Subontology)
    ))

plot_data$description <- 
  factor(plot_data$description, levels = plot_data$description)

max_y <- max(plyr::round_any(plot_data$enrichment_factor, 10, f = ceiling))

p <- ggplot2::ggplot(
  plot_data, 
  ggplot2::aes( x = description, y = enrichment_factor, fill = qvalue) ) +
  ggplot2::geom_bar( stat = "identity" ) +
  ggplot2::xlab("") +
  ggplot2::ylab("Enrichment") +
  ggplot2::ylim(0, max_y) +
  ggplot2::theme_classic() +
  ggplot2::coord_flip() +
  ggplot2::theme(
    #legend.position = "none",
    legend.title = ggplot2::element_blank(),
    axis.text.x = ggplot2::element_text(size = plot_fontsize, vjust = 0.5),
    axis.text.y = ggplot2::element_text(family = "Helvetica", size = plot_fontsize),
    axis.title.x = ggplot2::element_text(family = "Helvetica", size = plot_fontsize),
    axis.title.y = ggplot2::element_text(family = "Helvetica", size = plot_fontsize)
  )

rm(max_y)

height_plot <- 500
if (nrow(plot_data) <= 15) {
  height_plot <- 400
}
if (nrow(plot_data) <= 10) {
  height_plot <- 300
}

enrichment_barplot <- plotly::ggplotly(p, width = 800, height = height_plot) |>
    plotly::layout(legend = list(orientation = "h", x = -0.2, y = -0.25))

enrichment_barplot
rm(height_plot)
rm(plot_data)

```

```{r go_plot_missing_cc}
#| echo: false
#| output: asis
#| eval: !expr subontology_plots[['CC']] == FALSE

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;Enrichment plot omitted: No/limited GO terms were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
:::

<br><br>
