### Query verification


```{r imperfect_stop_notice}
#| output: asis
#| echo: false
#| eval: !expr onc_enrich_report[['data']][['query']]$validation_status == "imperfect_stop"

cat('<br><br>\n <span style="font-size:110%; line-height:110%; padding:3px; background-color:#800026; color:white">&nbsp;<b> - IMPORTANT NOTICE:</b> Due to invalid entries in the query set, analysis is halted.&nbsp;&nbsp;<br>&nbsp;&nbsp; - Set <i>\'Ignore errenous identifiers (ignore_id_err)\'</i> = TRUE in order to ignore invalid entries and complete the analysis &nbsp;&nbsp; with <i>oncoEnrichR</i>.&nbsp;&nbsp; </span>',sep='\n')
cat('\n')
cat('<br><br>')

```
   
::: {.callout-note}
## Identifier mapping results

* A total of __n = `r NROW(onc_enrich_report[['data']][['query']][['target']])`__ target identifiers were provided (type: _`r onc_enrich_report[['config']][['query']][['id_type']]`_, option _ignore_id_err_ = `r onc_enrich_report[["config"]][["query"]][["ignore_err"]]`)
* All query identifiers have been mapped towards identifiers for known human genes (including non-ambiguous aliases), and valid/invalid entries in the query set are indicated as follows:
   * <span style="background-color:#005a32; line-height:110%; padding:2x; color:white"><b>&nbsp; Valid identifier &nbsp; </b></span> &nbsp;:&nbsp;&nbsp; __n = `r NROW(onc_enrich_report[['data']][['query']][['target']] |> dplyr::filter(status == 'found'))`__
   * <span style="background-color:#238b45; line-height:110%; padding:2x; color:white"><b>&nbsp; Valid identifier (mapped as alias) &nbsp; </b></span> &nbsp;:&nbsp;&nbsp; __n = `r NROW(onc_enrich_report[['data']][['query']][['target']] |> dplyr::filter(status == 'found_as_alias'))`__
   * <span style="background-color:#800026; line-height:110%; padding:2x; color:white"><b>&nbsp; Invalid identifier &nbsp; </b></span> &nbsp;:&nbsp;&nbsp; __n = `r NROW(onc_enrich_report[['data']][['query']][['target']] |> dplyr::filter(status == 'not_found'))`__

::: 

<br>


```{r table_browse_querylist}
#| echo: false
#| output: asis
#| eval: true

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['query']][['target']], escape = F, 
              extensions=c("Buttons","Responsive"), 
              width = "100%",
              options=list(buttons = c('csv','excel'), 
                           dom = 'Bfrtip')) |>
  DT::formatStyle(columns = c("query_id"),
                  valueColumns = c('status'),
                  color = "white", 
                  backgroundColor = DT::styleEqual(
                  c('found','not_found','found_as_alias'), 
                  c("#005a32","#800026","#238b45"))
  )


```

<br><br>
