### Subcellular compartments 

::: {.callout-note}
## Synopsis

* The query set is annotated with data from [COMPARTMENTS](https://compartments.jensenlab.org/Search), a weekly updated database of subcellular localization data for human proteins, and results are here presented in two different views:

   1. A subcellular _anatogram_ - acting as a "heatmap" of subcellular structures associated with proteins in the query set
       * Compartments are here limited to the key compartments (n = 24) defined within the [gganatogram package](https://github.com/jespermaag/gganatogram#cellular-structures)
   2. A subcellular _data browser_
       * All unique subcellular compartment annotations and their target members ("By Compartment")
       * Subcellular compartment annotations per gene are provided with a __confidence score__ between 3 and 5 - indicating the quality/reliability of a given compartment annotation
          * Minimum confidence score (pr. COMPARTMENTS channel) - user-provided: __`r onc_enrich_report$config$subcellcomp$minimum_confidence`__
          * Minimum number of supporting COMPARTMENTS channels pr. annotation - user-provided: __`r onc_enrich_report$config$subcellcomp$minimum_channels`__
          * Ignore cytosol as a subcellular location: __`r !onc_enrich_report$config$subcellcomp$show_cytosol`__

:::

<br>

#### Subcellular anatogram

::: {.panel-tabset}

##### Heatmap - query set

<br>

* In the heatmap below, *value* refers to the fraction of target genes that are annotated with a particular compartment/subcellular structure
<br><br>

```{r gganatogram_plot}
#| echo: false
#| output: asis
#| eval: !expr as.logical(NROW(onc_enrich_report[['data']][['subcellcomp']][['anatogram']]) > 0) == TRUE
#| fig-width: 10
#| fig-height: 5

suppressPackageStartupMessages(library(gganatogram))

subcellcomp_geneset_density <- 
  onc_enrich_report[['data']][['subcellcomp']][['anatogram']]

if(onc_enrich_report[['config']][['subcellcomp']][['show_cytosol']] == F){
  subcellcomp_geneset_density <- 
    subcellcomp_geneset_density |>
    dplyr::filter(organ != "cytosol")
}

gganatogram::gganatogram(data = subcellcomp_geneset_density,
                         outline = T,
                         fillOutline = 'lightgray',
                         organism = 'cell',
                         fill = 'value') +
  ggplot2::theme_void() +
  ggplot2::coord_fixed() +
  ggplot2::scale_fill_gradient(low ="#FFEDA0", high = "#800026")

```
<br><br>

```{r subcellcomp_density_barplot}
#| echo: false
#| output: asis
#| eval: !expr as.logical(NROW(onc_enrich_report[['data']][['subcellcomp']][['anatogram']]) > 0) == TRUE

plot_data <- onc_enrich_report[['data']][['subcellcomp']][['anatogram']] |>
  dplyr::arrange(value)
plot_data$organ <- factor(plot_data$organ, levels = plot_data$organ)
plot_data$toDownlight <- "NO"

if(onc_enrich_report[['config']][['subcellcomp']][['show_cytosol']] == F){
  plot_data <- plot_data |>
    dplyr::mutate(toDownlight = dplyr::if_else(
      organ == "cytosol",
      as.character("YES"),
      as.character(toDownlight)
    ))
}

p <- ggplot2::ggplot(
  plot_data, 
  ggplot2::aes( x = organ, y = value, fill = toDownlight) ) +
  ggplot2::geom_bar( stat = "identity" ) +
  ggplot2::ylab("Percent of query gene set") +
  ggplot2::scale_fill_manual(
    values = c("YES"="gray", "NO"="BLACK" ), guide = FALSE ) +
  ggplot2::xlab("") +
  ggplot2::ylim(0,100) +
  ggplot2::theme_classic() +
  ggplot2::coord_flip() +
  ggplot2::theme(
    legend.position = "none",
    axis.text.x = ggplot2::element_text(size = 11, vjust = 0.5),
    legend.text = ggplot2::element_text(face="bold", family = "Helvetica", size = 11),
    axis.text.y = ggplot2::element_text(family = "Helvetica", size = 11),
    axis.title.x = ggplot2::element_text(family = "Helvetica", size = 11),
    axis.title.y = ggplot2::element_text(family = "Helvetica", size = 11)
  )

plotly::ggplotly(p, width = 600, height = 600)

```



:::

#### Subcellular data browser

<br>

::: {.panel-tabset}

##### By compartment

* Genes listed per compartment are calculated using only compartment annotations with a minimum confidence level (pr. channel) of: __`r onc_enrich_report$config$subcellcomp$minimum_confidence`__

<br>

```{r table_browse_subcell_comp_grouped}
#| echo: false
#| output: asis
#| eval: !expr as.logical(NROW(onc_enrich_report[['data']][['subcellcomp']][['grouped']]) > 0) == TRUE

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['subcellcomp']][['grouped']], 
              escape = F, extensions=c("Buttons","Responsive"), 
              width = "100%",
  options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))


```
<br><br><br>

:::

