### Subcellular compartments 

::: {.callout-note}
## Synopsis

* The query set is annotated with data from [COMPARTMENTS](https://compartments.jensenlab.org/Search), a weekly updated database of subcellular localization data for human proteins, and results are here presented in two different views:

   1. An interactive subcellular compartment heatmap - indicating compartments dominant within the query set
   2. A subcellular _data browser_
       * All unique subcellular compartment annotations and their target members ("By Compartment")
       * Subcellular compartment annotations per gene are provided with a __confidence score__ between 3 and 5 - indicating the quality/reliability of a given compartment annotation
          * Minimum confidence score (pr. COMPARTMENTS channel) - user-provided: __`r onc_enrich_report$config$subcellcomp$minimum_confidence`__
          * Minimum number of supporting COMPARTMENTS channels pr. annotation - user-provided: __`r onc_enrich_report$config$subcellcomp$minimum_channels`__
          * Ignore cytosol as a subcellular location: __`r !onc_enrich_report$config$subcellcomp$show_cytosol`__

:::

<br>

#### Subcellular anatogram

<br>

* In the anotogram below, color reflects the fraction of all target genes (importantly, limited to those that _have_ subcellular compartment annotations from COMPARTMENTS) that are annotated with a particular compartment/subcellular structure
<br><br>

```{r bscui_plot}
#| echo: false
#| output: asis
#| eval: !expr as.logical(NROW(onc_enrich_report[['data']][['subcellcomp']][['comp_density']]) > 0) == TRUE
#| fig-width: 14
#| fig-height: 12

suppressPackageStartupMessages(library(bscui))

subcellcomp_geneset_density <- 
  onc_enrich_report[['data']][['subcellcomp']][['comp_density']]

if(onc_enrich_report[['config']][['subcellcomp']][['show_cytosol']] == F){
  subcellcomp_geneset_density <- 
    subcellcomp_geneset_density |>
    dplyr::filter(name != "Cytosol")
}

fig <- oncoEnrichR::subcell_map$figure |>
  bscui::set_bscui_ui_elements(oncoEnrichR::subcell_map$ui_elements) |>
  bscui::set_bscui_styles(
    dplyr::select(
      subcellcomp_geneset_density,
      c("id", "fill")
    ),
  )

fig

```
<br><br>


```{r subcellcomp_density_barplot}
#| echo: false
#| output: asis
#| eval: !expr as.logical(NROW(onc_enrich_report[['data']][['subcellcomp']][['comp_density']]) > 0) == TRUE

plot_data <- 
  onc_enrich_report[['data']][['subcellcomp']][['comp_density']] |>
  dplyr::arrange(proportion) |>
  dplyr::mutate(percent = proportion * 100) |>
  tail(25)
plot_data$name <- factor(plot_data$name, levels = plot_data$name)
plot_data$toDownlight <- "NO"

if(onc_enrich_report[['config']][['subcellcomp']][['show_cytosol']] == F){
  plot_data <- plot_data |>
    dplyr::mutate(toDownlight = dplyr::if_else(
      name == "Cytosol",
      as.character("YES"),
      as.character(toDownlight)
    ))
}

p <- ggplot2::ggplot(
  plot_data, 
  ggplot2::aes( x = name, y = percent, fill = toDownlight) ) +
  ggplot2::geom_bar( stat = "identity" ) +
  ggplot2::ylab("Percent of query gene set") +
  ggplot2::scale_fill_manual(
    values = c("YES"="gray", "NO"="black" ), guide = FALSE ) +
  ggplot2::xlab("") +
  ggplot2::ylim(0,100) +
  ggplot2::theme_classic() +
  ggplot2::coord_flip() +
  ggplot2::theme(
    legend.position = "none",
    axis.text.x = ggplot2::element_text(size = 11, vjust = 0.5),
    legend.text = ggplot2::element_text(face="bold", family = "Helvetica", size = 11),
    axis.text.y = ggplot2::element_text(family = "Helvetica", size = 11),
    axis.title.x = ggplot2::element_text(family = "Helvetica", size = 11),
    axis.title.y = ggplot2::element_text(family = "Helvetica", size = 11)
  )

plotly::ggplotly(p, width = 600, height = 800)

```



#### Subcellular data browser

<br>

::: {.panel-tabset}

##### By compartment

* Genes listed per compartment are calculated using only compartment annotations with a minimum confidence level (pr. channel) of: __`r onc_enrich_report$config$subcellcomp$minimum_confidence`__

* A maximum of **n = 75** genes annotated to each compartment are shown here - sorted by their strength of association to cancer (all compartment genes are listed in the Excel workbook)

<br>

```{r table_browse_subcell_comp_grouped}
#| echo: false
#| output: asis
#| eval: !expr as.logical(NROW(onc_enrich_report[['data']][['subcellcomp']][['grouped']]) > 0) == TRUE

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['subcellcomp']][['grouped']], 
              escape = F, extensions=c("Buttons","Responsive"), 
              width = "100%",
  options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))


```
<br><br><br>

:::

