### Cancer hallmark evidence

* Each gene in the query set is annotated with cancer hallmarks evidence ([Hanahan & Weinberg, Cell, 2011](https://pubmed.ncbi.nlm.nih.gov/21376230/)), indicating genes associated with essential alterations in cell physiology that can dictate malignant growth.
* Data has been collected from the [Open Targets Platform](https://targetvalidation.org), and we list evidence for each hallmark per gene, indicated as either being <span style="background-color:#005a32; color:white"><b>&nbsp;promoted &nbsp;</b></span>, or <span style="background-color:#800026; color:white"><b>&nbsp;suppressed &nbsp; </b></span>

<br><br>


```{r table_browse_hallmarks, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['cancer_hallmark']][['target']]) > 0}

target_hm_shared <- crosstalk::SharedData$new(
  onc_enrich_report[['data']][['cancer_hallmark']][['target']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("hallmark", "Cancer hallmark", target_hm_shared, ~hallmark)
  )
)

htmltools::br()
DT::datatable(target_hm_shared, 
              escape = F, 
              extensions=c("Buttons","Responsive"), 
              width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip')) |>
  DT::formatStyle(columns = c("promotes"),
                  valueColumns = c('promotes'),
                  color = "white", 
                  backgroundColor = DT::styleEqual(
                  c(TRUE, FALSE), 
                  c("#005a32","#989898"))
  ) |>
   DT::formatStyle(columns = c("suppresses"),
                  valueColumns = c('suppresses'),
                  color = "white", 
                  backgroundColor = DT::styleEqual(
                  c(TRUE, FALSE), 
                  c("#800026","#989898"))
  )



```


```{r hallmarks_missing, echo=F, results = 'asis', eval = NROW(onc_enrich_report[['data']][['cancer_hallmark']][['target']]) == 0}

cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> query genes with cancer hallmark associations from Open Targets Platform were found. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>
