### Cancer associations {.tabset}

* Each target in the query set is annotated with:
   * Known associations to cancer phenotypes (_ontology terms_) established from [multiple data types](https://platform-docs.opentargets.org/associations#association-scores) through the [Open Targets Platform](https://targetvalidation.org). Annotations are provided both through descriptive associations and numerical rank scores
   * Classification with respect to roles as tumor suppressors, proto-oncogenes, and cancer driver genes
        * Cancer driver genes need support from either [Network of Cancer Genes](http://ncg.kcl.ac.uk/) or [IntOGen](https://www.intogen.org)
        * Tumor suppressor genes and proto-oncogenes require support from either the [CancerMine](https://www.nature.com/articles/s41592-019-0422-y) literature mining resource (>= 15 citations), the [Network of Cancer Genes](http://ncg.kcl.ac.uk/), or the [Cancer Gene Census](https://cancer.sanger.ac.uk/census)
        * Classifications are ignored for genes found in a curated list of [false positive driver predictions](https://pubmed.ncbi.nlm.nih.gov/29625053/)
   * Gene function summary - retrieved from [NCBI](https://www.ncbi.nlm.nih.gov/gene) and [UniProt Knowledgebase](https://www.uniprot.org/)
 
<br><br>


#### Query set - cancer association rank

<br>

* Query set genes are ranked according to their overall strength of association to cancer, visualized in varying shades of blue (from <span style="background-color:#b8b8ba; padding:2x; color:white"><b>&nbsp; weak associations &nbsp; </b></span>&nbsp; to <span style="background-color:#08306b; padding:2x; color:white"><b>&nbsp; strong associations &nbsp; </b></span>). Specifically, ranking is based on the sum of [association scores](https://docs.targetvalidation.org/getting-started/scoring) pr. tumor type/tissue, and scaled as percent rank within the query set (column **targetset_cancer_rank**)

<br><br>

```{r table_browse_targets, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['disease']][['target']]) > 0}

target_assocs <- onc_enrich_report[['data']][['disease']][['target']] |>
  dplyr::select(-c(.data$oncogene_evidence,
                    .data$tumor_suppressor_evidence,
                    .data$cancer_driver_evidence))

targets_shared <- crosstalk::SharedData$new(target_assocs)

crosstalk::bscols(
  list(
    crosstalk::filter_select("symbol", "Target", targets_shared, ~symbol),
    crosstalk::filter_checkbox("tumor_suppressor", "Tumor suppressor", targets_shared, ~tumor_suppressor),
    crosstalk::filter_checkbox("oncogene", "Proto-oncogene", targets_shared, ~oncogene)
  ),
  list(
    crosstalk::filter_select("cancer_associations", "Associated cancer types", targets_shared, ~cancer_associations),
    crosstalk::filter_select("disease_associations", "Associated diseases (non-cancer)", targets_shared, ~disease_associations),
    crosstalk::filter_checkbox("cancer_driver", "Cancer driver gene", targets_shared, ~cancer_driver)
  )
)

htmltools::br()
DT::datatable(targets_shared, escape = F, 
              extensions=c("Buttons","Responsive"), 
              width = "100%",
              options=list(buttons = c('csv','excel'),
                           pageLength = 20,
                           dom = 'Blfrtip')) |>
  DT::formatStyle("symbol",
                  "targetset_cancer_rank", 
                  color = "white", 
                  backgroundColor = DT::styleInterval(
                    onc_enrich_report[['config']][['disease']][['breaks']],
                    onc_enrich_report[['config']][['disease']][['colors']])
  )


```


```{r opentargets_missing, echo=F, results = 'asis', eval = NROW(onc_enrich_report[['data']][['disease']][['target']]) == 0}
cat('<i>No genes with disease associations from Open Targets Platform were found.</i>',sep='\n')
cat('\n')
```


<br><br>

#### Query set - association strength pr. tumor type

* Top cancer-associated genes (maximum 100) in the query set are shown with their specific tumor-type association strengths (percent rank)

<br><br>

```{r target_ttype_heatmap, echo = F, eval = nrow(onc_enrich_report[['data']][['disease']][['ttype_matrix']]) > 2 & ncol(onc_enrich_report[['data']][['disease']][['ttype_matrix']]) > 2}

oe_ttype_matrix <- 
  onc_enrich_report[['data']][['disease']][['ttype_matrix']]

if(NROW(oe_ttype_matrix) > 100){
  oe_ttype_matrix <- oe_ttype_matrix[1:100,]
}

if(NROW(oe_ttype_matrix) > 1){
  oe_ttype_matrix <- 
    oe_ttype_matrix[nrow(oe_ttype_matrix):1, ]
}

n_percent_ticks <- 10
if(NROW(oe_ttype_matrix) < 20){
  n_percent_ticks <- 5
}

#plotly_colors <- "Blues"

target_ttype_rank_fig <- plotly::plot_ly(
  colors = "Blues",
  width = 800,
  height = 400 + (14.67 * NROW(oe_ttype_matrix))) |>
  plotly::add_heatmap(
    y = rownames(oe_ttype_matrix),
    x = colnames(oe_ttype_matrix),
    z = oe_ttype_matrix,
    hovertext = "Tumor type percent rank",
    yaxis = "y") |>
  plotly::layout(
    title = 'Tumor type association rank',
    xaxis = list(tickfont = list(size = 13, family = "Helvetica"), 
                 tickangle = -50),
    yaxis = list(tickfont = list(size = 12, family = "Helvetica")),
    margin = list(l = 75, r = 20, b = 150, t = 30, pad = 4)
  ) |>
  plotly::colorbar(
    nticks = n_percent_ticks, 
    title = list(text = "Percent rank",side = "bottom"),
    limits = c(0, plyr::round_any(max(oe_ttype_matrix), 100, ceiling)))

rm(oe_ttype_matrix)
target_ttype_rank_fig


```

```{r missing_ttype_ranked_associations, echo=F, results = "asis", eval = nrow(onc_enrich_report[['data']][['disease']][['ttype_matrix']]) <= 2 | ncol(onc_enrich_report[['data']][['disease']][['ttype_matrix']]) <= 2}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NOT SHOWN</b> - limited/few tumor-type specific associations found for genes in the query set.&nbsp;&nbsp;</span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
<br><br>
