### Documentation and settings

The configurations set for this oncoEnrichR report is outlined below, in addition to an overview of knowledge resources used. 

#### Configuration values for `onco_enrich()` 

* <i>General:</i>
  * `html_report_theme` = __`r onc_enrich_report[['config']][['rmarkdown']][['theme']]`__
  * `html_floating_toc` = __`r onc_enrich_report[['config']][['rmarkdown']][['floating_toc']]`__
  * `query_id_type` = __`r onc_enrich_report[['config']][['query']][['id_type']]`__
  * `bgset_id_type` = __`r onc_enrich_report[['config']][['bgset']][['id_type']]`__
  * `bgset_description` = __`r onc_enrich_report[['config']][['enrichment']][['bgset_description']]`__

* <i>Modules included in report</i>:

  * `show_disease` = __`r onc_enrich_report[['config']][['show']][['disease']]`__
  * `show_drugs` = __`r onc_enrich_report[['config']][['show']][['drug']]`__
  * `show_cancer_hallmarks` = __`r onc_enrich_report[['config']][['show']][['cancer_hallmark']]`__
  * `show_fitness` = __`r onc_enrich_report[['config']][['show']][['fitness']]`__
  * `show_complex` = __`r onc_enrich_report[['config']][['show']][['protein_complex']]`__
  * `show_unknown_function` = __`r onc_enrich_report[['config']][['show']][['unknown_function']]`__
  * `show_domain` = __`r onc_enrich_report[['config']][['show']][['protein_domain']]`__
  * `show_synleth` = __`r onc_enrich_report[['config']][['show']][['synleth']]`__
  * `show_ligand_receptor` = __`r onc_enrich_report[['config']][['show']][['ligand_receptor']]`__
  * `show_regulatory` = __`r onc_enrich_report[['config']][['show']][['regulatory']]`__
  * `show_subcellcomp` = __`r onc_enrich_report[['config']][['show']][['subcellcomp']]`__
  * `show_enrichment` = __`r onc_enrich_report[['config']][['show']][['enrichment']]`__
  * `show_cell_tissue` = __`r onc_enrich_report[['config']][['show']][['cell_tissue']]`__
  * `show_coexpression` = __`r onc_enrich_report[['config']][['show']][['coexpression']]`__
  * `show_aberration` = __`r onc_enrich_report[['config']][['show']][['aberration']]`__
  * `show_prognostic` = __`r onc_enrich_report[['config']][['show']][['cancer_prognosis']]`__
  * `show_ppi` = __`r onc_enrich_report[['config']][['show']][['ppi']]`__

* <i>Cancer associations:</i>
  * `show_top_diseases_only` = __`r onc_enrich_report[['config']][['disease']][['show_top_diseases']]`__

* <i>Regulatory interactions:</i>
  * `regulatory_min_confidence` = __`r onc_enrich_report[['config']][['regulatory']][['min_confidence']]`__

* <i>Subcellular compartments:</i>
  * `subcellcomp_min_confidence` = __`r onc_enrich_report[['config']][['subcellcomp']][['minimum_confidence']]`__
  * `subcellcomp_min_channels` = __`r onc_enrich_report[['config']][['subcellcomp']][['minimum_channels']]`__
  * `subcellcomp_channel_types` = __`r onc_enrich_report[['config']][['subcellcomp']][['channels']]`__
  * `subcellcomp_show_cytosol` = __`r onc_enrich_report[['config']][['subcellcomp']][['show_cytosol']]`__

* <i>Gene fitness scores:</i>
  * `fitness_max_score` = __`r onc_enrich_report[['config']][['fitness']][['max_BF_score']]`__

* <i>Enrichment:</i>
  * `enrichment_p_value_cutoff` = __`r onc_enrich_report[['config']][['enrichment']][['p_value_cutoff']]`__
  * `enrichment_q_value_cutoff` = __`r onc_enrich_report[['config']][['enrichment']][['q_value_cutoff']]`__
  * `enrichment_p_value_adj` = __`r onc_enrich_report[['config']][['enrichment']][['p_adjust_method']]`__
  * `enrichment_min_geneset_size` = __`r onc_enrich_report[['config']][['enrichment']][['min_gs_size']]`__
  * `enrichment_max_geneset_size` = __`r onc_enrich_report[['config']][['enrichment']][['max_gs_size']]`__
  * `enrichment_simplify_go` = __`r onc_enrich_report[['config']][['enrichment']][['simplify_go']]`__
  * `enrichment_plot_num_terms` = __`r onc_enrich_report[['config']][['enrichment']][['enrichment_plot_num_terms']]`__

* <i>Protein-protein interactions:</i>
  * `ppi_string_min_score` = __`r onc_enrich_report[['config']][['ppi']][['string']][['minimum_score']]`__
  * `ppi_string_network_type` = __`r onc_enrich_report[['config']][['ppi']][['string']][['network_type']]`__
  * `ppi_biogrid_min_evidence` = __`r onc_enrich_report[['config']][['ppi']][['biogrid']][['minimum_evidence']]`__
  * `ppi_add_nodes` = __`r onc_enrich_report[['config']][['ppi']][['string']][['add_nodes']]`__
  * `ppi_node_shadow` = __`r onc_enrich_report[['config']][['ppi']][['string']][['visnetwork_shadow']]`__
  * `ppi_show_drugs` = __`r onc_enrich_report[['config']][['ppi']][['string']][['show_drugs']]`__
  * `ppi_show_isolated_nodes` = __`r onc_enrich_report[['config']][['ppi']][['string']][['show_isolated_nodes']]`__

<br>

#### Annotation resources

The analysis performed in the _oncoEnrichR report_ is based on the following main tools and knowledge resources:

* __Software__ 
```{r list_software, echo=F,results='asis'}
for(n in names(onc_enrich_report[['config']][['resources']])){
  if(onc_enrich_report[['config']][['resources']][[n]]$resource_type == 'software'){
    s <- paste0('    * [',onc_enrich_report[['config']][['resources']][[n]]$name,'](',onc_enrich_report[['config']][['resources']][[n]]$url,') - ',onc_enrich_report[['config']][['resources']][[n]]$description, ' (',onc_enrich_report[['config']][['resources']][[n]]$version,')')
    cat(s,sep="\n")
  }
}

```
<br><br>

* __Databases/datasets__ 
```{r list_db, echo=F,results='asis'}
for(n in names(onc_enrich_report[['config']][['resources']])){
  if(onc_enrich_report[['config']][['resources']][[n]]$resource_type != 'software'){
      s <- paste0('    * [',onc_enrich_report[['config']][['resources']][[n]]$name,'](',onc_enrich_report[['config']][['resources']][[n]]$url,') - ',onc_enrich_report[['config']][['resources']][[n]]$description, ' (',onc_enrich_report[['config']][['resources']][[n]]$version,')')
      cat(s,sep="\n")
  }
}

```
