### Drug associations

* Each protein/protein in the query set is annotated with:
   * Molecularly targeted drugs (i.e. small molecule inhibitors/antagonists or monoclonal antibodies), as found through the [Open Targets Platform](https://targetvalidation.org) and the [NCI Thesaurus](https://ncithesaurus.nci.nih.gov/ncitbrowser/)
   * Drugs are organized into the following buckets:
       * Targeted cancer drugs in early clinical development/phase (phase 1-2)(column <b>drugs_early_phase</b>)
       * Targeted cancer drugs in late clinical development/phase (phase 3-4) (column <b>drugs_late_phase</b>)
       * <i>Approved drugs</i> - here also showing the (cancer type) indications for which the drugs are approved for

<br><br>


```{r table_browse_drug_targets, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['drug']][['target_drugs']]) > 0}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['drug']][['target_drugs']], escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))



```


```{r drug_targets_missing, echo=F, results = 'asis', eval = NROW(onc_enrich_report[['data']][['drug']][['target_drugs']]) == 0}

cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> query proteins with cancer drug associations from Open Targets Platform were found. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br>

#### Target tractabilities {.tabset }

* Each gene/protein in the query set is annotated with _[target tractability information](https://docs.targetvalidation.org/getting-started/target-tractability)_ (also known as _druggability_) towards
small molecules/compounds and antibodies
* Query genes are colored in varying shades of purple (from <span style="background-color:#b8b8ba; padding:2x; color:white">&nbsp;unknown tractability&nbsp;</span> to <span style="background-color:#810f7c; padding:2x; color:white">&nbsp;clinical precedence&nbsp;</span>)
   

<br><br>

##### Small molecules/compounds 

```{r table_browse_tractability_sm, echo=F, results = "asis", eval = T}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['drug']][['tractability_sm']], escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), dom = 'Bfrtip')) |>
   DT::formatStyle(
    "SM_tractability_category", 
    color = "white",
    backgroundColor = DT::styleEqual(
      onc_enrich_report[["config"]][["drug"]][["sm_levels"]],
      onc_enrich_report[["config"]][["drug"]][["sm_levels_colors"]]
    )
  )



```


##### Antibodies

```{r table_browse_tractability_ab, echo=F, results = "asis", eval = T}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['drug']][['tractability_ab']], escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), dom = 'Bfrtip')) |>
   DT::formatStyle(
    "AB_tractability_category", 
    color = "white",
    backgroundColor = DT::styleEqual(
      onc_enrich_report[["config"]][["drug"]][["ab_levels"]],
      onc_enrich_report[["config"]][["drug"]][["ab_levels_colors"]]
    )
  )



```

<br><br>

### {.unlisted .unnumbered .toc-ignore}

<span style="font-size: 100%; padding: 2px; background-color:#014587; color:white">&nbsp;&nbsp;<b>Citation Note</b>&nbsp;&nbsp;</span> : If you use the output of the *Drug associations* module of oncoEnrichR in your research, please cite the following resources and tools:

 * [Nakken et al., arXiv, 2022](https://arxiv.org/abs/2107.13247) - *oncoEnrichR*
 * [Ochoa et al., Nucleic Acids Res, 2021](https://pubmed.ncbi.nlm.nih.gov/33196847/) - *Open Targets Platform*
 * [Sioutos et al., J Biomed Inform, 2007](https://pubmed.ncbi.nlm.nih.gov/16697710/) - *NCI Thesaurus*

<br><br><br>

