### Ligand-receptor interactions {.tabset}

<br>

* Using data from the [CellChatDB](http://www.cellchat.org/) resource, we are here interrogating ligand-receptor interactions for members of the query set. Putative interactions are displayed along three different axes with respect to cell-cell comunication:

   1) Secreted Signaling (Paracrine/autocrine signaling)
   2) ECM-Receptor (extracellular matrix-receptor interactions)
   3) Cell-Cell Contact


<br><br>

#### Secreted Signaling


```{r lig_rec_interactions_1, echo = F, results = 'asis', eval = nrow(onc_enrich_report[['data']][['ligand_receptor']][['secreted_signaling']]) > 0}

ligand_interactions_ss <- 
  crosstalk::SharedData$new(onc_enrich_report[['data']][['ligand_receptor']][['secreted_signaling']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("ligand", "Ligand", ligand_interactions_ss, ~ligand)
  ),
  list(
    crosstalk::filter_select("receptor", "Receptor", ligand_interactions_ss, ~receptor)
  )
)

htmltools::br()

DT::datatable(
  ligand_interactions_ss, 
  escape = F, 
  extensions=c("Buttons","Responsive"), 
  width = "100%",
  style = 'bootstrap',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  )


```
<br><br>


```{r no_lig_receptor_interactions1, echo=F, results = 'asis', eval = nrow(onc_enrich_report[['data']][['ligand_receptor']][['secreted_signaling']]) == 0}
cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> pair of genes in the queryset are involved in ligand-receptor interactions (<b>CellChatDB - Secreted signalling</b>)&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br>

#### ECM-Receptor


```{r lig_rec_interactions_2, echo = F, results = 'asis', eval = nrow(onc_enrich_report[['data']][['ligand_receptor']][['ecm_receptor']]) > 0}

ligand_interactions_ecm <- 
  crosstalk::SharedData$new(onc_enrich_report[['data']][['ligand_receptor']][['ecm_receptor']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("ligand", "Ligand", ligand_interactions_ecm, ~ligand)
  ),
  list(
    crosstalk::filter_select("receptor", "Receptor", ligand_interactions_ecm, ~receptor)
  )
)

htmltools::br()

DT::datatable(
  ligand_interactions_ecm, 
  escape = F, 
  extensions=c("Buttons","Responsive"), 
  width = "100%",
  style = 'bootstrap',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  )


```
<br><br>


```{r no_lig_receptor_interactions2, echo=F, results = 'asis', eval = nrow(onc_enrich_report[['data']][['ligand_receptor']][['ecm_receptor']]) == 0}
cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> pair of genes in the queryset are involved in ligand-receptor interactions (<b>CellChatDB - ECM Receptor</b>)&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>

#### Cell-Cell Contact


```{r lig_rec_interactions_3, echo = F, results = 'asis', eval = nrow(onc_enrich_report[['data']][['ligand_receptor']][['cell_cell_contact']]) > 0}

ligand_interactions_ccc <- 
  crosstalk::SharedData$new(onc_enrich_report[['data']][['ligand_receptor']][['cell_cell_contact']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("ligand", "Ligand", ligand_interactions_ccc, ~ligand)
  ),
  list(
    crosstalk::filter_select("receptor", "Receptor", ligand_interactions_ccc, ~receptor)
  )
)

htmltools::br()

DT::datatable(
  ligand_interactions_ccc, 
  escape = F, 
  extensions=c("Buttons","Responsive"), 
  width = "100%",
  style = 'bootstrap',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  )


```
<br><br>


```{r no_lig_receptor_interactions3, echo=F, results = 'asis', eval = nrow(onc_enrich_report[['data']][['ligand_receptor']][['cell_cell_contact']]) == 0}
cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> pair of genes in the queryset are involved in ligand-receptor interactions (<b>CellChatDB - Cell-Cell Contact</b>)&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>
