### Protein-protein interaction network

* We here create dedicated protein-protein interaction networks for members of the query set, shown based on interaction data from the two largest resources of protein-protein interaction data:
  * [BioGRID](https://thebiogrid.org) - a biomedical interaction repository with data compiled through comprehensive curation efforts
  * [STRING](https://string-db.org/cgi/about?footer_active_subpage=content) - database of known and predicted protein-protein interactions, including direct (physical) and indirect (functional) associations
  * Three different views are shown for each resource:
    * Complete protein-protein interaction network, also showing proteins with no known interactions
    * Network community structures, as detected by the fast greedy modularity optimization algorithm by [Clauset et al.](http://www.arxiv.org/abs/cond-mat/0408187)
    * Network centrality/hub scores pr. node, as measured by [Kleinberg's score](https://dl.acm.org/citation.cfm?id=324140)
  
<br>

* General network legend:
  * Target set proteins are shaped as **circles**, other interacting proteins are shaped as **rectangles** (note that sizes of nodes do not carry any value), drugs are shaped as **diamonds**
  * Tumor suppressor genes (as classified from [Network of Cancer Genes/Cancer Gene Census/CancerMine](https://sigven.github.io/oncoEnrichR/articles/annotation_resources.html#tumor-suppressoroncogenedriver-annotation)) are <span style="color:firebrick"><b>HIGHLIGHTED IN RED</b></span>
  * Proto-oncogenes (as classified from [Network of Cancer Genes/Cancer Gene Census/CancerMine](https://sigven.github.io/oncoEnrichR/articles/annotation_resources.html#tumor-suppressoroncogenedriver-annotation)) are <span style="color:darkolivegreen"><b>HIGHLIGHTED IN GREEN</b></span>
  * Genes predicted to have a dual role as proto-oncogenes/tumor suppressors are <span style="color:black"><b>HIGHLIGHTED IN BLACK</b></span>
  * Targeted cancer drugs (from [Open Targets Platform](https://targetvalidation.org)):
     * Compounds in late (3-4) clinical development phases are <span style="color:orange"><b>HIGHLIGHTED IN ORANGE</b></span>
     * Compounds in early (1-2) clinical development phases are <span style="color:purple"><b>HIGHLIGHTED IN PURPLE</b></span>
  * Use the mouse to zoom in/out, alter the position of nodes, mouse-over edges and nodes to view gene names/drug mechanism of actions (with indications)/interaction scores (evidence support)

<br><br>

#### PPI network - STRING {.tabset}

<br>

  * STRING interaction network type: __`r onc_enrich_report[['config']][['ppi']][['string']][['network_type']]`__
    * This reflects the `network_type` parameter in the [STRING API](https://string-db.org/cgi/help.pl?subpage=api%23getting-the-string-network-interactions)
  * The STRING network is expanded with __n = `r onc_enrich_report[['config']][['ppi']][['string']][['add_nodes']]`__ proteins that interact with proteins in the query set
    * This reflects the `add_nodes` parameter in the [STRING API](https://string-db.org/cgi/help.pl?subpage=api%23getting-the-string-network-interactions)
  * Minimum STRING [interaction confidence score](https://string-db.org/cgi/info) required: __`r onc_enrich_report[['config']][['ppi']][['string']][['minimum_score']]`__ (range 0-1)
    * This reflects the `required_score` parameter in the [STRING API](https://string-db.org/cgi/help.pl?subpage=api%23getting-the-string-network-interactions)
  * Drugs added to the STRING network: __`r onc_enrich_report[['config']][['ppi']][['string']][['show_drugs']]`__ 
  * Show isolated nodes in the STRING network: __`r onc_enrich_report[['config']][['ppi']][['string']][['show_isolated_nodes']]`__

<br>

##### Complete network

```{r ppi_string_complete_network, echo = F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['string']][['complete_network']]$nodes) > 0, fig.width = 12, fig.height=13}
visNetwork::visNetwork(onc_enrich_report[['data']][['ppi']][['string']][['complete_network']]$nodes, 
                       onc_enrich_report[['data']][['ppi']][['string']][['complete_network']]$edges) |>
  visNetwork::visInteraction(multiselect=TRUE, tooltipDelay=300) |>
  visNetwork::visIgraphLayout(layout="layout_nicely")

```


```{r ppi_string_complete_network_missing, echo=F, results = "asis", eval = nrow(onc_enrich_report[['data']][['ppi']][['string']][['complete_network']]$nodes) == 0}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No protein-protein interactions from STRING were found among members in the query set (with the required association score). Lowering the assocation score threshold of for interactions in STRING may provide a network. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>

##### Network communities

```{r ppi_string_network_community, echo = F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['string']][['community_network']]$nodes) > 0 & NROW(onc_enrich_report[['data']][['ppi']][['string']][['community_network']]$edges) > 0, fig.width = 12, fig.height=13}
visNetwork::visNetwork(
  onc_enrich_report[['data']][['ppi']][['string']][['community_network']]$nodes, 
  onc_enrich_report[['data']][['ppi']][['string']][['community_network']]$edges) |>
  visNetwork::visInteraction(multiselect=TRUE, tooltipDelay=300) |>
  visNetwork::visIgraphLayout(layout="layout_nicely")

```

```{r ppi_string_missing_network_community, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['string']][['community_network']]$nodes) == 0 | NROW(onc_enrich_report[['data']][['ppi']][['string']][['community_network']]$edges) == 0}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No network communities were found among members in the query set (with the required association score). Lowering the assocation score threshold of for interactions in STRING may provide a network and associated communities. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
<br><br>

##### Network hubs

```{r table_string_browse_ppi_hubs, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['string']]$hubscores) > 0}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['ppi']][['string']][['hubscores']], 
              escape = F, extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip', pagelength = 20)) |>
  DT::formatStyle("symbol","hub_score", color = "white", backgroundColor = DT::styleInterval(onc_enrich_report[['config']][['disease']][['breaks']], onc_enrich_report[['config']][['disease']][['colors']]))



```

```{r table_string_browse_ppi_hubs_missing, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['string']]$hubscores) == 0}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No hubscores from the protein-protein interaction network were established for members in the query set (with the required association score). Lowering the assocation score threshold of for interactions in STRING may provide a network with hubscores. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
<br><br>

#### PPI network - BioGRID {.tabset}

<br>

  * The BioGRID network is expanded with __n = `r onc_enrich_report[['config']][['ppi']][['biogrid']][['add_nodes']]`__ targets that are not part of the query set, but that interact with members of the query set
    * These targets are selected based on the number of interactions that they have with members of the query set
  * Minimum evidence support required for each BioGRID interaction: __`r onc_enrich_report[['config']][['ppi']][['biogrid']][['minimum_evidence']]`__ 
  * Drugs added to the BioGRID network: __`r onc_enrich_report[['config']][['ppi']][['biogrid']][['show_drugs']]`__ 
  * Show isolated nodes in the BioGRID network: __`r onc_enrich_report[['config']][['ppi']][['biogrid']][['show_isolated_nodes']]`__

  
<br>
  
##### Complete network

```{r ppi_biogrid_complete_network, echo = F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['biogrid']][['complete_network']]$nodes) > 0, fig.width = 12, fig.height=13}
visNetwork::visNetwork(
  onc_enrich_report[['data']][['ppi']][['biogrid']][['complete_network']]$nodes, 
  onc_enrich_report[['data']][['ppi']][['biogrid']][['complete_network']]$edges) |>
  visNetwork::visInteraction(multiselect=TRUE, tooltipDelay=300) |>
  visNetwork::visIgraphLayout(layout="layout_nicely")

```


```{r ppi_biogrid_complete_network_missing, echo=F, results = "asis", eval = nrow(onc_enrich_report[['data']][['ppi']][['biogrid']][['complete_network']]$nodes) == 0}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No protein-protein interactions from BioGRID were found among members in the query set (with the required evidence support). Lowering the required evidence support for interactions in BioGRID may provide a network. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>

##### Network communities

```{r ppi_biogrid_network_community, echo = F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['biogrid']][['community_network']]$nodes) > 0 & NROW(onc_enrich_report[['data']][['ppi']][['biogrid']][['community_network']]$edges) > 0, fig.width = 12, fig.height=13}
visNetwork::visNetwork(
  onc_enrich_report[['data']][['ppi']][['biogrid']][['community_network']]$nodes, 
  onc_enrich_report[['data']][['ppi']][['biogrid']][['community_network']]$edges) |>
  visNetwork::visInteraction(multiselect=TRUE, tooltipDelay=300) |>
  visNetwork::visIgraphLayout(layout="layout_nicely")

```

```{r ppi_biogrid_missing_network_community, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['biogrid']][['community_network']]$nodes) == 0 | NROW(onc_enrich_report[['data']][['ppi']][['biogrid']][['community_network']]$edges) == 0}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No network communities were found among members in the query set (with the required evidence support). Lowering the required evidence support for interactions in BioGRID may provide a network and associated communities. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
<br><br>

##### Network hubs

```{r table_biogrid_browse_ppi_hubs, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['biogrid']]$hubscores) > 0}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['ppi']][['biogrid']][['hubscores']], 
              escape = F, extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip', pagelength = 20)) |>
  DT::formatStyle("symbol","hub_score", color = "white", 
                  backgroundColor = DT::styleInterval(
                    onc_enrich_report[['config']][['disease']][['breaks']],                                                                                           onc_enrich_report[['config']][['disease']][['colors']])
  )



```

```{r table_biogrid_browse_ppi_hubs_missing, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['ppi']][['biogrid']]$hubscores) == 0}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No hubscores from the protein-protein interaction network were established for members in the query set (with the required evidence support). Lowering the required evidence support for interactions in BioGRID may provide a network with hubscores. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
<br><br>

