### Protein complexes {.tabset}

* Here we show how members of the query set that are involved in *known* protein complexes, using two different collections of protein complex annotations:

  1. [OmniPath](https://omnipathdb.org/) - a meta-database of molecular biology prior knowledge, containing protein complex annotations predominantly from [CORUM](http://mips.helmholtz-muenchen.de/corum/), [ComplexPortal](https://www.ebi.ac.uk/complexportal/home), [Compleat](https://fgr.hms.harvard.edu/compleat), and [PDB](https://www.rcsb.org/).
     * We limit complex annotations to those that are supported by references to the scientific literature (i.e. manually curated)
  2. [Human Protein Complex Map - hu.MAP v2.0](http://humap2.proteincomplexes.org/)  - created through an integration of > 15,000 proteomics experiments (biochemical fractionation data, proximity labeling data, and RNA hairpin pulldown data)
     * Each complex comes with a confidence score from clustering (1=Extremely High, 2=Very High, 3=High, 4=Medium High, 5=Medium)
   
* The protein complexes that overlap with members of the query set are ranked according to the total number of participating members in the query set
   
<br><br>

```{r complex_prep, echo = F, results = 'asis', eval = T}

active_tab <- list()

for(cl in c('omnipath','humap2')){
  active_tab[[cl]] <- F
}

if(NROW(onc_enrich_report[['data']][['protein_complex']][['omnipath']]) > 0){
  active_tab[['omnipath']] <- T
}else{
  if(NROW(onc_enrich_report[['data']][['protein_complex']][['humap2']]) > 0){
    active_tab[['humap2']] <- T
  }else{
    active_tab[['omnipath']] <- T
  }
}

  
```

```{r active_tab_omnipath, echo = F, results = "asis"}
if(active_tab[['omnipath']] == T){
  cat("")
  cat("#### OmniPath {.active}")
  cat("")
}else{
  cat("")
  cat("#### OmniPath")
  cat("")
}
```

```{r table_browse_complex_omnipath, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['protein_complex']][['omnipath']]) > 0}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['protein_complex']][['omnipath']], 
              escape = F, 
              extensions=c("Buttons","Responsive"), 
              width = "100%",
              style = 'bootstrap',
              rownames = F,
              options=list(buttons = c('csv','excel'),
                           pageLength = 10,
                           bPaginate = T,
                           dom = 'Bfrtip') 
)


```


```{r indicate_missing_complexes, echo=F, results = 'asis', eval = NROW(onc_enrich_report[['data']][['protein_complex']][['omnipath']]) == 0}

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO GENES</b> in the query set associate with protein complexes found in the OmniPath database .&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br>

```{r active_tab_humap2, echo = F, results = "asis"}
if(active_tab[['humap2']] == T){
  cat("")
  cat("#### hu.MAP v2.0 {.active}")
  cat("")
}else{
  cat("")
  cat("#### hu.MAP v2.0")
  cat("")
}
```

```{r table_browse_complex_humap2, echo=F, results = "asis", eval = NROW(onc_enrich_report[['data']][['protein_complex']][['humap2']]) > 0}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['protein_complex']][['humap2']], 
              escape = F, 
              extensions=c("Buttons","Responsive"), 
              width = "100%",
              style = 'bootstrap',
              rownames = F,
              options=list(buttons = c('csv','excel'),
                           pageLength = 10,
                           bPaginate = T,
                           dom = 'Bfrtip') 
)


```


```{r indicate_missing_complexes_humap2, echo=F, results = 'asis', eval = NROW(onc_enrich_report[['data']][['protein_complex']][['humap2']]) == 0}

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO GENES</b> in the query set associate with protein complexes established by the <b>hu.MAP v2.0</b> protein complex map .&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br>
