### Synthetic lethality

<br>

* Using recently published predictions on synthetic lethal interactions in human cancer cell lines ([De Kegel et al., Cell Syst., 2021](https://pubmed.ncbi.nlm.nih.gov/34529928/)), we here show whether members of the query set are found among these interactions.
* Note that predictions in the study by *Kegel et al.* are provided for human gene paralogs only
* In the tables below, predictions below the 50% percentile are ignored (the complete set can be found in the Excel output of oncoEnrichR). Additional properties of each predicted pair of interactors are included for filtering, including:
  * Prediction score and percentile
  * Percent sequence identity between the genes
  * Size of gene paralog family
  
* The higher the prediction score, the more confident the prediction is with respect to a synthetic lethality interaction. Interactions are here ranked according to confidence (percentile), visualized in varying shades of blue (from <span style="background-color:#b8b8ba; padding:2x; color:white"><b>&nbsp; low-confident interactions &nbsp; </b></span>&nbsp; to <span style="background-color:#08306b; padding:2x; color:white"><b>&nbsp; high-confident interactions &nbsp; </b></span>).


<br><br>

```{r synleth_prep, echo = F, results = 'asis', eval = T}

sl_interactions <- list()
sl_interactions[['a_b']] <- data.frame()
sl_interactions[['a_only']] <- data.frame()
active_tab <- list()
active_tab[['a_b']] <- F
active_tab[['a_only']] <- F

if(NROW(onc_enrich_report[['data']][['synleth']][['both_in_pair']]) > 0){
  sl_interactions[['a_b']] <- onc_enrich_report[['data']][['synleth']][['both_in_pair']] %>%
    dplyr::filter(.data$prediction_percentile < 50) %>%
    head(2500)
  
  active_tab[['a_b']] <- T

}

if(NROW(onc_enrich_report[['data']][['synleth']][['single_pair_member']]) > 0){
  sl_interactions[['a_only']] <- onc_enrich_report[['data']][['synleth']][['single_pair_member']] %>%
    dplyr::filter(.data$prediction_percentile < 50) %>%
    head(2500)
  
  if(active_tab[['a_b']] == F){
    active_tab[['a_only']] <- T
  }
  
}


```


#### Predicted synthetic lethality interactions {.tabset}

<br>

```{r active_tab_a_b, echo = F, results = "asis"}
if(active_tab[['a_b']] == T){
  cat("")
  cat("##### Both pair members in query set {.active}")
  cat("")
}else{
  cat("")
  cat("##### Both pair members in query set")
  cat("")
}
```

```{r synleth_interactions_1, echo = F, results = 'asis', eval = nrow(sl_interactions[['a_b']]) > 0}

sl_ab <- 
  crosstalk::SharedData$new(sl_interactions[['a_b']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("gene_A", "Interactor A", sl_ab, ~gene_A),
    crosstalk::filter_select("gene_B", "Interactor B", sl_ab, ~gene_B),
    crosstalk::filter_slider("prediction_score", "Prediction score", sl_ab, ~prediction_score,
                             step = 0.025, min = 0.0, max = 0.45),
    crosstalk::filter_slider("prediction_percentile", "Prediction percentile", sl_ab, ~prediction_percentile,
                             min = 0.0, step = 2, max = 50)
  ),
  list(
    crosstalk::filter_slider("sequence_identity_pct", "Sequence identity (percent)", sl_ab, ~sequence_identity_pct,
                             min = 0, max = 100),
    crosstalk::filter_slider("family_size", "Gene family size", sl_ab, ~family_size)
  )
)

htmltools::br()

DT::datatable(
  sl_ab, 
  escape = F, 
  extensions=c("Buttons","Responsive"), 
  width = "100%",
  style = 'bootstrap',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  ) %>%
   DT::formatStyle("gene_A",
                  "prediction_percentile", 
                  color = "white", 
                  backgroundColor = DT::styleInterval(
                    onc_enrich_report[['config']][['synleth']][['breaks']],
                    onc_enrich_report[['config']][['synleth']][['colors']])
  ) %>%
  DT::formatStyle("gene_B",
                  "prediction_percentile", 
                  color = "white", 
                  backgroundColor = DT::styleInterval(
                    onc_enrich_report[['config']][['synleth']][['breaks']],
                    onc_enrich_report[['config']][['synleth']][['colors']])
  )


```
<br><br>


```{r sl_interactions_missing_1, echo=F, results = 'asis', eval = nrow(sl_interactions[['a_b']]) == 0}
cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> genes in the queryset are involved in synthetic lethality interactions for which <b>BOTH</b> member pairs are part of the queryset.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>

```{r active_tab_a_only, echo = F, results = "asis"}
if(active_tab[['a_only']] == T){
  cat("")
  cat("##### Single pair member in query set {.active}")
  cat("")
}else{
  cat("")
  cat("##### Single pair member in query set")
  cat("")
}
```

```{r sl_interactions_2, echo = F, results = 'asis', eval = nrow(sl_interactions[['a_only']]) > 0}

sl_a <- 
  crosstalk::SharedData$new(sl_interactions[['a_only']])


crosstalk::bscols(
  list(
    crosstalk::filter_select("gene_A", "Interactor A", sl_a, ~gene_A),
    crosstalk::filter_select("gene_B", "Interactor B", sl_a, ~gene_B),
    crosstalk::filter_slider("prediction_score", "Prediction score", sl_a, ~prediction_score,
                             step = 0.025, min = 0.0, max = 0.45),
    crosstalk::filter_slider("prediction_percentile", "Prediction percentile", sl_a, ~prediction_percentile,
                             min = 0.0, step = 2, max = 50)
  ),
  list(
    crosstalk::filter_slider("sequence_identity_pct", "Sequence identity (percent)", sl_a, ~sequence_identity_pct,
                             min = 0, max = 100),
    crosstalk::filter_slider("family_size", "Gene family size", sl_a, ~family_size)
  )
)

htmltools::br()

DT::datatable(
  sl_a, 
  escape = F, 
  extensions=c("Buttons","Responsive"), 
  width = "100%",
  style = 'bootstrap',
  rownames = F,
  options=list(buttons = c('csv','excel'),
               pageLength = 10,
               bPaginate = T,
               dom = 'Bfrtip')
  ) %>%
   DT::formatStyle("gene_A",
                  "prediction_percentile", 
                  color = "white", 
                  backgroundColor = DT::styleInterval(
                    onc_enrich_report[['config']][['synleth']][['breaks']],
                    onc_enrich_report[['config']][['synleth']][['colors']])
  )


```
<br><br>


```{r sl_interactions_missing_2, echo=F, results = 'asis', eval = nrow(sl_interactions[['a_only']]) == 0}
cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> genes in the queryset are involved in prediced synthetic lethal interactions for which <b>ONLY</b> a single member pair is part of the queryset.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>
