### Poorly characterized query members

* The aim of this section is to highlight poorly characterized genes or genes with unknown function in the query set
* A set of _uncharacterized/poorly characterized human protein-coding genes (__n = `r NROW(oncoEnrichR::genedb[['poorly_defined']])`__) _ have been established based on
   1. Genes specifically designated as uncharacterized or as _open reading frames_
   2. Missing gene function summary in [NCBI Gene](https://www.ncbi.nlm.nih.gov/gene) AND function summary in [UniProt Knowledgebase](https://uniprot.org)
   2. Missing or limited (<= 2) [gene ontology (GO) annotations](https://www.ebi.ac.uk/GOA/human_release) with respect to molecular function (MF) and biological process (BP)
      * Ontology annotations attributed with an [electronic annotation evidence code (IEA)](http://geneontology.org/docs/guide-go-evidence-codes/) are not considered in this calculation (less reliable due to lack of manually review)
      
* Query genes found within the set of poorly characterized genes are listed below, colored in varying shades of red according to the level of missing characterization (from <span style="background-color:#99000d; padding:2x; color:white">&nbsp;unknown function&nbsp;</span> to <span style="background-color:#fcbba1; padding:2x; color:white">&nbsp;poorly defined function&nbsp;</span>)
   
<br><br>



```{r filter_unknown, echo=F, results='asis'}

show_ufunction_genes <- FALSE

if(nrow(onc_enrich_report[['data']][['unknown_function']][['hits_df']]) > 0){
  show_ufunction_genes <- TRUE
}

```


```{r table_browse_unknown, echo=F, results = "asis", eval = show_ufunction_genes}
library(crosstalk)

targets_unknown_function <- crosstalk::SharedData$new(onc_enrich_report[['data']][['unknown_function']][['hits_df']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("symbol", "Target", targets_unknown_function, ~symbol),
    crosstalk::filter_checkbox("has_gene_summary", "Has gene summary", targets_unknown_function, ~has_gene_summary)
  ),
  list(
    crosstalk::filter_slider("num_go_annotations", "Number of annotated GO terms (non-IEA)", targets_unknown_function, ~num_go_terms)
  )
)

htmltools::br()
DT::datatable(targets_unknown_function, 
              escape = F, 
              extensions=c("Buttons","Responsive"), 
              width = "100%",
              options=list(buttons = c('csv','excel'), 
                           dom = 'Bfrtip')) %>%
  
  DT::formatStyle(
    "symbol",
    "unknown_function_rank", 
    color = "white",
    backgroundColor = DT::styleEqual(
      onc_enrich_report[["config"]][["unknown_function"]][["rank"]],
      onc_enrich_report[["config"]][["unknown_function"]][["colors"]]
    )
  )


```


```{r ufunction_genes_missing, echo=F, results = 'asis', eval = !show_ufunction_genes}
cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> genes with unknown or poorly defined functions were detected in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br>
