### Drug associations

* Each protein/protein in the query set is annotated with:
   * Targeted cancer drugs (inhibitors/antagonists), as found through the [Open Targets Platform](https://targetvalidation.org)
   * We distinguish between drugs in <i>early clinical development/phase (<b>ep</b>)</i>, and drugs already in <i>late clinical development/phase (<b>lp</b>)</i>

<br><br>


```{r filter_drug_targets, echo=F, results='asis'}

show_drug_targets <- FALSE
missing_drug_targets <- TRUE

if(nrow(onc_enrich_report[['data']][['drug']][['target_drugs']]) > 0){
  show_drug_targets <- TRUE
  missing_drug_targets <- FALSE
}

```



```{r table_browse_drug_targets, echo=F, results = "asis", eval = show_drug_targets}
library(crosstalk)

targets_shared <- onc_enrich_report[['data']][['drug']][['target_drugs']]

htmltools::br()
DT::datatable(targets_shared, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))



```


```{r drug_targets_missing, echo=F, results = 'asis', eval = missing_drug_targets}

cat('\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;<b>NO</b> query proteins with cancer drug associations from Open Targets Platform were found. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br>

#### Target tractabilities {.tabset }

* Each gene/protein in the query set is annotated with _[target tractability information](https://docs.targetvalidation.org/getting-started/target-tractability)_ (aka druggability) towards
small molecules/compounds and antibodies
* Query genes are colored in varying shades of purple (from <span style="background-color:#b8b8ba; padding:2x; color:white">&nbsp;unknown tractability&nbsp;</span> to <span style="background-color:#810f7c; padding:2x; color:white">&nbsp;clinical precedence&nbsp;</span>)
   

<br><br>

##### Small molecules/compounds 

```{r table_browse_tractability_sm, echo=F, results = "asis", eval = T}
library(crosstalk)

tractabilities_sm_shared <- onc_enrich_report[['data']][['drug']][['tractability_sm']]

htmltools::br()
DT::datatable(tractabilities_sm_shared, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), dom = 'Bfrtip')) %>%
   DT::formatStyle(
    "SM_tractability_category", 
    color = "white",
    backgroundColor = DT::styleEqual(
      onc_enrich_report[["config"]][["drug"]][["sm_levels"]],
      onc_enrich_report[["config"]][["drug"]][["sm_levels_colors"]]
    )
  )



```


##### Antibodies

```{r table_browse_tractability_ab, echo=F, results = "asis", eval = T}
library(crosstalk)

tractabilities_ab_shared <- onc_enrich_report[['data']][['drug']][['tractability_ab']]

htmltools::br()
DT::datatable(tractabilities_ab_shared, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), dom = 'Bfrtip')) %>%
   DT::formatStyle(
    "AB_tractability_category", 
    color = "white",
    backgroundColor = DT::styleEqual(
      onc_enrich_report[["config"]][["drug"]][["ab_levels"]],
      onc_enrich_report[["config"]][["drug"]][["ab_levels_colors"]]
    )
  )



```

