### Function and pathway enrichment {.tabset}

* Each protein in the query set is analyzed with [clusterProfiler](https://bioconductor.org/packages/release/bioc/vignettes/clusterProfiler/inst/doc/clusterProfiler.html) for functional enrichment/overrepresentation with respect to:
   * [Gene Ontology terms](https://geneontology.org). All three subontologies: _Molecular Function_ (GO_MF), _Cellular Component_ (GO_CC) & _Biological Process_ (GO_BP)
   * Molecular signalling networks from [KEGG](https://www.genome.jp/kegg/pathway.html)
   * Cellular pathways from [Reactome](https://reactome.org/), and other curated gene signature sets from the [Molecular Signatures Database (MSiGDB)](http://software.broadinstitute.org/gsea/msigdb/index.jsp)
   * [WikiPathways](https://www.wikipathways.org/index.php/Special:BrowsePathways)
   * Manually curated signal transduction pathways from [NetPath](http://www.netpath.org)
  
<br>

* Enrichment/overrepresentation test settings
   * P-value cutoff: `r onc_enrich_report[['config']][['enrichment']][['p_value_cutoff']]`
   * Q-value cutoff: `r onc_enrich_report[['config']][['enrichment']][['q_value_cutoff']]`
   * Correction for multiple testing: `r onc_enrich_report[['config']][['enrichment']][['p_adjust_method']]`
   * Minimal size of genes annotated by term for testing: `r onc_enrich_report[['config']][['enrichment']][['min_gs_size']]`
   * Maximal size of genes annotated by term for testing: `r onc_enrich_report[['config']][['enrichment']][['max_gs_size']]`
   * Background gene set: `r onc_enrich_report[['config']][['enrichment']][['bgset_description']]`
   

<br><br>


```{r prepare_enrichment_data, echo=F, results='asis'}

show_enrichment_filters <- list()
missing_enrichment_items <- list()
eitems <- list()
for(type in c('go','msigdb','wikipathway','kegg','netpath')){
  show_enrichment_filters[[type]] <- F
  missing_enrichment_items[[type]] <- T
  if(NROW(onc_enrich_report[['data']][['enrichment']][[type]]) > 0){
    show_enrichment_filters[[type]] <- T
    missing_enrichment_items[[type]] <- F
  }
}

```


#### Gene Ontology

```{r table_browse_go, echo=F, results = "asis", eval = show_enrichment_filters[['go']]}
library(crosstalk)

enrichment_go_display <- onc_enrich_report[['data']][['enrichment']][['go']] %>%
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, Q_Value = qvalue, P_Value = pvalue, 
                Gene_Members = gene_symbol_link, DB = db,
                Exact_Source = exact_source, Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio, Count = count,
                P_Value_Cutoff = setting_p_value_cutoff,
                Q_Value_Cutoff = setting_q_value_cutoff,
                P_Value_Adj_Method = setting_p_value_adj_method,
                Min_Geneset_Size = setting_min_geneset_size,
                Max_Geneset_Size = setting_max_geneset_size) %>%
   dplyr::select(Term, Enrichment, Q_Value, Gene_Members, DB, Exact_Source, 
                Background_Ratio, Gene_Ratio, Count, P_Value_Cutoff, Q_Value_Cutoff,
                P_Value_Adj_Method, Min_Geneset_Size, Max_Geneset_Size)


terms_go <- crosstalk::SharedData$new(enrichment_go_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_go, ~Enrichment)
  ),
  list(
    crosstalk::filter_select("DB", "Ontology", terms_go, ~DB)

  )
)

htmltools::br()
DT::datatable(terms_go, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
)


```

```{r go_missing, echo=F, results = 'asis', eval = missing_enrichment_items[['go']]}

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No gene ontology terms were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br><br>

#### Molecular Signatures Database (MSigDB)

```{r table_browse_msigdb, echo=F, results = "asis", eval = show_enrichment_filters[['msigdb']]}
library(crosstalk)

enrichment_msigdb_display <- onc_enrich_report[['data']][['enrichment']][['msigdb']] %>%
  dplyr::rename(Term = description_link, Enrichment = enrichment_factor, Q_Value = qvalue,  P_Value = pvalue,
                Gene_Members = gene_symbol_link, DB = db,
                Exact_Source = exact_source, Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio, Count = count,
                P_Value_Cutoff = setting_p_value_cutoff,
                Q_Value_Cutoff = setting_q_value_cutoff,
                P_Value_Adj_Method = setting_p_value_adj_method,
                Min_Geneset_Size = setting_min_geneset_size,
                Max_Geneset_Size = setting_max_geneset_size) %>%
  dplyr::select(Term, Enrichment, Q_Value, Gene_Members, DB, Exact_Source, 
                Background_Ratio, Gene_Ratio, Count, P_Value_Cutoff, Q_Value_Cutoff,
                P_Value_Adj_Method, Min_Geneset_Size, Max_Geneset_Size)

terms_msigdb <- crosstalk::SharedData$new(enrichment_msigdb_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_msigdb, ~Enrichment)
  ),
  list(
    crosstalk::filter_select("DB", "Signature collection", terms_msigdb, ~DB)

  )
)

htmltools::br()
DT::datatable(terms_msigdb, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'), 
                           dom = 'Bfrtip')
)

```


```{r msigdb_missing, echo=F, results = 'asis', eval = missing_enrichment_items[['msigdb']]}

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No signatures from the Molecular Signature Database (MSIGdb) were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br><br>

#### KEGG

```{r table_browse_kegg, echo=F, results = "asis", eval = show_enrichment_filters[['kegg']]}
library(crosstalk)

enrichment_keggdb_display <- onc_enrich_report[['data']][['enrichment']][['kegg']] %>%
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue,  
                P_Value = pvalue,
                Gene_Members = gene_symbol_link, 
                DB = db,
                Exact_Source = exact_source, 
                Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio, Count = count,
                P_Value_Cutoff = setting_p_value_cutoff,
                Q_Value_Cutoff = setting_q_value_cutoff,
                P_Value_Adj_Method = setting_p_value_adj_method,
                Min_Geneset_Size = setting_min_geneset_size,
                Max_Geneset_Size = setting_max_geneset_size) %>%
  dplyr::select(Term, Enrichment, Q_Value, Gene_Members, DB, Exact_Source, 
                Background_Ratio, Gene_Ratio, Count, P_Value_Cutoff, Q_Value_Cutoff,
                P_Value_Adj_Method, Min_Geneset_Size, Max_Geneset_Size)

terms_keggdb <- crosstalk::SharedData$new(enrichment_keggdb_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_keggdb, ~Enrichment)
  )
)

htmltools::br()
DT::datatable(terms_keggdb, escape = F, extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
)


```


```{r keggdb_missing, echo=F, results = 'asis', eval = missing_enrichment_items[['kegg']]}

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No pathways from KEGG  were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```


<br><br><br>


#### WikiPathways

```{r table_browse_wikipathwaydb, echo=F, results = "asis", eval = show_enrichment_filters[['wikipathway']]}
library(crosstalk)

enrichment_wikidb_display <- onc_enrich_report[['data']][['enrichment']][['wikipathway']] %>%
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue, P_Value = pvalue,
                Gene_Members = gene_symbol_link, DB = db,
                Exact_Source = exact_source, Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio, Count = count,
                P_Value_Cutoff = setting_p_value_cutoff,
                Q_Value_Cutoff = setting_q_value_cutoff,
                P_Value_Adj_Method = setting_p_value_adj_method,
                Min_Geneset_Size = setting_min_geneset_size,
                Max_Geneset_Size = setting_max_geneset_size) %>%
   dplyr::select(Term, Enrichment, Q_Value, Gene_Members, 
                 DB, Exact_Source, 
                Background_Ratio, Gene_Ratio, Count, 
                P_Value_Cutoff, Q_Value_Cutoff,
                P_Value_Adj_Method, 
                Min_Geneset_Size, Max_Geneset_Size)


terms_wikipathway <- crosstalk::SharedData$new(enrichment_wikidb_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_wikipathway, ~Enrichment)
  )
)

htmltools::br()
DT::datatable(terms_wikipathway, escape = F, extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
)



```


```{r wiki_missing, echo=F, results = 'asis', eval = missing_enrichment_items[['wikipathway']]}

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No pathway signatures from WikiPathways were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')


```


<br><br><br>

#### NetPath

```{r table_browse_netpathdb, echo=F, results = "asis", eval = show_enrichment_filters[['netpath']]}
library(crosstalk)

enrichment_netpath_display <- onc_enrich_report[['data']][['enrichment']][['netpath']] %>%
  dplyr::rename(Term = description_link, 
                Enrichment = enrichment_factor, 
                Q_Value = qvalue, P_Value = pvalue,
                Gene_Members = gene_symbol_link, DB = db,
                Exact_Source = exact_source, Background_Ratio = background_ratio, 
                Gene_Ratio = gene_ratio, Count = count,
                P_Value_Cutoff = setting_p_value_cutoff,
                Q_Value_Cutoff = setting_q_value_cutoff,
                P_Value_Adj_Method = setting_p_value_adj_method,
                Min_Geneset_Size = setting_min_geneset_size,
                Max_Geneset_Size = setting_max_geneset_size) %>%
   dplyr::select(Term, Enrichment, Q_Value, Gene_Members, 
                 DB, Exact_Source, 
                Background_Ratio, Gene_Ratio, Count, 
                P_Value_Cutoff, Q_Value_Cutoff,
                P_Value_Adj_Method, 
                Min_Geneset_Size, Max_Geneset_Size)

terms_netpath <- crosstalk::SharedData$new(enrichment_netpath_display)

crosstalk::bscols(
  list(
    crosstalk::filter_slider("Enrichment", "Enrichment", terms_netpath, ~Enrichment)
  )
)

htmltools::br()
DT::datatable(terms_netpath, escape = F, extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
)



```


```{r netpath_missing, echo=F, results = 'asis', eval = missing_enrichment_items[['netpath']]}

cat('<br><br>\n <ul><li>  <i> <span style="font-size: 105%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No signalling pathways from NetPath were enriched in the query set.&nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')


```


<br><br><br>
