### Protein-protein interaction network {.tabset}

* The query set is queried against known protein-protein interactions, as evident from the [STRING API (v11)](http://string-db.org)
  * Note that interactions in STRING are assembled from multiple sources, including co-expression, co-occurrence in the literature, experimental data, curated databases etc
  * In addition to potential interactions within the query set, the network is expanded with __n = `r onc_enrich_report[['config']][['ppi']][['stringdb']][['add_nodes']]`__ proteins that interact with proteins in the query set
  * Network is here restricted to interactions with __STRING association score >= `r onc_enrich_report[['config']][['ppi']][['stringdb']][['minimum_score']]`__ (range 0-1000))
  * Drugs added to the network: __`r onc_enrich_report[['config']][['ppi']][['stringdb']][['show_drugs']]`__ 
  * Three different views are shown
    * Complete protein-protein interaction network, also showing proteins with no known interactions
    * Network community structures, as detected by the fast greedy modularity optimization algorithm by [Clauset et al.](http://www.arxiv.org/abs/cond-mat/0408187)
    * Network centrality/hub scores pr. node, as measured by [Kleinberg's score](https://dl.acm.org/citation.cfm?id=324140)
  
<br>

* Network legend:
  * Target set proteins are shaped as **circles**, other interacting proteins are shaped as **rectangles** (note that sizes of nodes do not carry any value), drugs are shaped as **diamonds**
  * Tumor suppressor genes (annotated from [CancerMine](https://www.nature.com/articles/s41592-019-0422-y)) are <span style="color:firebrick"><b>HIGHLIGHTED IN RED</b></span>
  * Proto-oncogenes (annotated from [CancerMine](https://www.nature.com/articles/s41592-019-0422-y)) are <span style="color:darkolivegreen"><b>HIGHLIGHTED IN GREEN</b></span>
  * Genes predicted to have a dual role as proto-oncogenes/tumor suppressors (annotated from [CancerMine](https://www.nature.com/articles/s41592-019-0422-y)) are <span style="color:black"><b>HIGHLIGHTED IN BLACK</b></span>
  * Targeted cancer drugs (from [Open Targets Platform](https://targetvalidation.org)):
     * Compounds in late (3-4) clinical phases are <span style="color:orange"><b>HIGHLIGHTED IN ORANGE</b></span>
     * Compounds in early (1-2) clinical phases are <span style="color:purple"><b>HIGHLIGHTED IN PURPLE</b></span>
  
<br>

* Use the mouse to zoom in/out, alter the position of nodes, mouse-over to view gene names/drug mechanism of actions (with indications)

<br><br>


```{r check_ppi_content, echo=F, results='asis'}

missing_ppi <- TRUE
missing_community <- TRUE
missing_hub_scores <- TRUE

if(nrow(onc_enrich_report[['data']][['ppi']][['complete_network']]$nodes) > 0){
  missing_ppi <- FALSE
}
if(nrow(onc_enrich_report[['data']][['ppi']][['community_network']]$nodes) > 0 &
   nrow(onc_enrich_report[['data']][['ppi']][['community_network']]$edges) > 0){
  missing_community <- FALSE
}
if(nrow(onc_enrich_report[['data']][['ppi']][['hubscores']]) > 0){
  missing_hub_scores <- FALSE
}

```


#### Complete network

```{r ppi_complete_network, echo = F, results = "asis", eval = !missing_ppi, fig.width = 12, fig.height=13}
visNetwork::visNetwork(onc_enrich_report[['data']][['ppi']][['complete_network']]$nodes, 
                       onc_enrich_report[['data']][['ppi']][['complete_network']]$edges) %>%
  visNetwork::visInteraction(multiselect=TRUE, tooltipDelay=300) %>%
  visNetwork::visIgraphLayout(layout="layout_nicely")

```


```{r ppi_complete_network_missing, echo=F, results = "asis", eval = missing_ppi}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No protein-protein interactions from STRING were found among members in the query set (with the required association score). Lowering the assocation score threshold of for interactions in STRING may provide a network. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```

<br><br>

#### Network communities

```{r ppi_network_community, echo = F, results = "asis", eval = !missing_community, fig.width = 12, fig.height=13}
visNetwork::visNetwork(onc_enrich_report[['data']][['ppi']][['community_network']]$nodes, 
                       onc_enrich_report[['data']][['ppi']][['community_network']]$edges) %>%
  visNetwork::visInteraction(multiselect=TRUE, tooltipDelay=300) %>%
  visNetwork::visIgraphLayout(layout="layout_nicely")

```

```{r ppi_network_community_missing, echo=F, results = "asis", eval = missing_community}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No network community were found among members in the query set (with the required association score). Lowering the assocation score threshold of for interactions in STRING may provide a network and associated communities. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
<br><br>

#### Network hubs

```{r table_browse_ppi_hubs, echo=F, results = "asis", eval = !missing_hub_scores}

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['ppi']][['hubscores']], 
              escape = F, extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip', pagelength = 20)) %>%
  DT::formatStyle("symbol","hub_score", color = "white", backgroundColor = DT::styleInterval(onc_enrich_report[['config']][['disease']][['breaks']], onc_enrich_report[['config']][['disease']][['colors']]))



```

```{r table_browse_ppi_hubs_missing, echo=F, results = "asis", eval = missing_hub_scores}
cat('<br>')
cat('\n <ul><li>  <i> <span style="font-size: 100%; padding: 3px; background-color:#989898; color:white">&nbsp;&nbsp;No hubscores from the protein-protein interaction network were established for members in the query set (with the required association score). Lowering the assocation score threshold of for interactions in STRING may provide a network with hubscores. &nbsp;&nbsp; </span></i></li></ul>',sep='\n')
cat('\n')
cat('<br><br>')

```
<br><br>

