### Subcellular structures/compartments 


* The target set is annotated with data from [ComPPI](http://comppi.linkgroup.hu/), a database of subcellular localization data for human proteins, and results are here presented in two different views:

   1. A subcellular _anatogram_ - acting as a "heatmap" of subcellular structures associated with proteins in the target set
       * Compartments are here limited to the key compartments (n = 24) defined within the [gganatogram package](https://github.com/jespermaag/gganatogram#cellular-structures)
   2. A subcellular _data browser_
       * All subcellular compartment annotations pr. protein in the target set ("By Gene")
       * All unique subcellular compartment annotations (unfiltered) and their target members ("By Compartment")

<br><br>


#### Subcellular anatogram

* In the image below, *value* refers to the fraction of target genes that are annotated with a particular compartment/subcellular structure
<br><br>
```{r gganatogram_plot, echo = F, results = "asis", eval = T, fig.width = 10, fig.height = 5}

suppressPackageStartupMessages(library(gganatogram))
gganatogram::gganatogram(data = onc_enrich_report[['data']][['subcellcomp']][['anatogram']],
                         outline = T,
                         fillOutline = 'lightgray',
                         organism = 'cell',
                         fill = 'value') +
  ggplot2::theme_void() +
  ggplot2::coord_fixed() +
  ggplot2::scale_fill_viridis_c()

```
<br><br>

#### Subcellular data browser{.tabset}
<br>

##### By Gene

```{r table_browse_subcell_comp_all, echo=F, results = "asis", eval = T}
library(crosstalk)


subcell_comp_all <- crosstalk::SharedData$new(onc_enrich_report[['data']][['subcellcomp']][['all']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("target_gene", "Target gene",subcell_comp_all,~symbol),
    crosstalk::filter_select("annotation_type", "Annotation type", subcell_comp_all, ~annotation_type)
  ),
  list(
    crosstalk::filter_select("annotation_source", "Annotation source", subcell_comp_all, ~annotation_source),
    crosstalk::filter_slider("n_sources", "Number of annotation soures (confidence)", subcell_comp_all, ~n_sources)
  )
)

htmltools::br()
crosstalk::bscols(
  DT::datatable(subcell_comp_all, escape = F, extensions=c("Buttons","Responsive"), width = "100%",
    options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
  )
)

```
<br><br><br>

##### By Compartment

```{r table_browse_subcell_comp_grouped, echo=F, results = "asis", eval = T}
library(crosstalk)

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['subcellcomp']][['grouped']], escape = F, extensions=c("Buttons","Responsive"), width = "100%",
  options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))


```
<br><br><br>



