### Subcellular structures/compartments 

<br>

* The target set is annotated with data from [ComPPI](http://comppi.linkgroup.hu/), a database of subcellular localization data for human proteins, and results are here presented in two different views:

   1. A subcellular _anatogram_ - acting as a "heatmap" of subcellular structures associated with proteins in the target set
       * Compartments are here limited to the key compartments (n = 24) defined within the [gganatogram package](https://github.com/jespermaag/gganatogram#cellular-structures)
       * An accompanying legend is also provided - depicting the locations of the various subcellular structures
   2. A subcellular _data browser_
       * All subcellular compartment annotations pr. protein in the target set ("By Gene")
       * All unique subcellular compartment annotations (unfiltered) and their target members ("By Compartment")
       * Subcellular compartment annotations per gene are provided with a __confidence level__ - indicating the number of different sources that support the compartment annotation
          * Minimum confidence level set by user: __`r onc_enrich_report$config$subcellcomp$minimum_confidence`__

<br><br>


#### Subcellular anatogram {.tabset}
<br>

##### Heatmap - target set
<br>

* In the image below, *value* refers to the fraction of target genes that are annotated with a particular compartment/subcellular structure
<br><br>

```{r gganatogram_plot, echo = F, results = "asis", eval = T, fig.width = 10, fig.height = 5}

suppressPackageStartupMessages(library(gganatogram))
gganatogram::gganatogram(data = onc_enrich_report[['data']][['subcellcomp']][['anatogram']],
                         outline = T,
                         fillOutline = 'lightgray',
                         organism = 'cell',
                         fill = 'value') +
  ggplot2::theme_void() +
  ggplot2::coord_fixed() +
  ggplot2::scale_fill_viridis_c()

```
<br><br>

##### Legend - subcellular structures
<br>
```{r gganatogram_legend, echo = F, results = "asis", eval = T, fig.width = 10, fig.height = 20}

suppressPackageStartupMessages(library(gganatogram))
ggpubr::ggarrange(plotlist = 
                    oncoEnrichR::subcellcomp$gganatogram_legend[1:24], 
                  ncol = 4, nrow = 6)

```

#### Subcellular data browser{.tabset}
<br>

##### By Gene

```{r table_browse_subcell_comp_all, echo=F, results = "asis", eval = T}
library(crosstalk)


subcell_comp_all <- 
  crosstalk::SharedData$new(onc_enrich_report[['data']][['subcellcomp']][['all']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("target_gene", "Target gene", 
                             subcell_comp_all,~symbol),
    crosstalk::filter_select("annotation_type", "Annotation type", 
                             subcell_comp_all, ~annotation_type)
  ),
  list(
    crosstalk::filter_select("annotation_source", "Annotation source", 
                             subcell_comp_all, ~annotation_source),
    crosstalk::filter_slider("confidence", 
                             "Confidence level (number of annotation soures)", 
                             subcell_comp_all, ~confidence)
  )
)

htmltools::br()
DT::datatable(subcell_comp_all, escape = F, 
              extensions=c("Buttons","Responsive"), width = "100%",
              options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
)


```
<br><br><br>

##### By Compartment

* Genes listed per compartment are calculated using only compartment annotations with a minimum confidence level of: __`r onc_enrich_report$config$subcellcomp$minimum_confidence` (number of sources)__

<br>

```{r table_browse_subcell_comp_grouped, echo=F, results = "asis", eval = T}
library(crosstalk)

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['subcellcomp']][['grouped']], 
              escape = F, extensions=c("Buttons","Responsive"), 
              width = "100%",
  options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))


```
<br><br><br>



