### Subcellular compartments {.tabset}

* The target set is annotated with data from [ComPPI](http://comppi.linkgroup.hu/), a cellular compartment-specific database of proteins, and results are here presented in two different views:

   1. All subcellular compartment annotations pr. protein in the target set ("By Gene")
   2. All unique subcellular compartment annotations and their target members ("By Compartment")

<br><br>

#### By Gene

```{r table_browse_subcell_comp_all, echo=F, results = "asis", eval = T}
library(crosstalk)


subcell_comp_all <- crosstalk::SharedData$new(onc_enrich_report[['data']][['subcellcomp']][['all']])

crosstalk::bscols(
  list(
    crosstalk::filter_select("target_gene", "Target gene",subcell_comp_all,~symbol),
    crosstalk::filter_select("annotation_type", "Annotation type", subcell_comp_all, ~annotation_type)
  ),
  list(
    crosstalk::filter_slider("n_sources", "Number of soures", subcell_comp_all, ~n_sources),
    crosstalk::filter_select("annotation_source", "Annotation source", subcell_comp_all, ~annotation_source)
  )
)

htmltools::br()
crosstalk::bscols(
  DT::datatable(subcell_comp_all, escape = F, extensions=c("Buttons","Responsive"), width = "100%",
    options=list(buttons = c('csv','excel'),dom = 'Bfrtip')
  )
)

```
<br><br><br>

#### By Compartment

```{r table_browse_subcell_comp_grouped, echo=F, results = "asis", eval = T}
library(crosstalk)

htmltools::br()
DT::datatable(onc_enrich_report[['data']][['subcellcomp']][['grouped']], escape = F, extensions=c("Buttons","Responsive"), width = "100%",
  options=list(buttons = c('csv','excel'),dom = 'Bfrtip'))


```
<br><br><br>



